---
title: "Mood and DMN 2gps"
author: "Jason"
created: "16/03/2020"
modified: "18/12/2020"
output: 
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

***

# OVERVIEW
Question this study addresses:

* are there any factors that differentiate healthy controls (HC) and chronic low back pain (CLBP) patients?

* Measures analyzed  
  * Pittsburg Sleep Questionnaire  
  * Epsworth Sleepiness Scale  
  * Insomnia Severity Index  
  * McGill Pain Questionnaire  
  * Beck Depression Inventory
  * Positive mood - Pre
  * Positive mood - post
  * Change in mood - positive
  * Negative mood - pre
  * negative mood - post
  * Change in mood negative

***

**NOTE: THE ANALYSES CONTAINED HEREIN WILL BE FOR A MANUSCRIPT BASED ON APS 2017.**  
**ADDITIONAL ANALYSES AND RESULTS FOR THE POSTER WILL BE IN A DIFFERENT FILE.**

***FIX THE TEXT BELOW***

## ABSTRACT
###  Title  
**Significant differences in sleep and depression among chronic pain groups: Implications for patient education**  

###  Purpose  


***


# START
```{r setup, include=FALSE, comment=""}
knitr::opts_chunk$set(echo = TRUE)
```

# LIBRARIES
```{r Libraries, eval=TRUE, echo=TRUE, results=FALSE, collapse=TRUE, message=FALSE}
# library(multcomp)
# library(knitr)
# library(readr)
library(formatR)
library(caret)
library(kableExtra)
library(psych)
library(corrplot)
library(janitor)
library(ggpubr)
library(ggsignif)
library(plyr)
library(reshape2)
library(tidyverse)
library(reprex)
library(here)
here()
dr_here(show_reason = FALSE)

```

```{r Functions, eval=TRUE, echo=FALSE, message=FALSE}
####  different color series		####
col1 <- colorRampPalette(c("#7F0000", "red", "#FF7F00",
						   "yellow", "white","cyan",
						   "#007FFF", "blue","#00007F"))
col2 <- colorRampPalette(c("#67001F", "#B2182B",
						   "#D6604D", "#F4A582",
						   "#FDDBC7", "#FFFFFF",
						   "#D1E5F0", "#92C5DE",
						   "#4393C3", "#2166AC", 
						   "#053061"))
col3 <- colorRampPalette(c("red", "white", "blue"))
col4 <- colorRampPalette(c("#7F0000", "red", "#FF7F00", 
						   "yellow", "#7FFF7F",
						   "cyan", "#007FFF", "blue",
						   "#00007F"))
wb <- c("white", "black")

####		DATE VARIABLE		####
currentDate <- format(Sys.time(), "%F_%H-%M")

####		APPEND DATE TO STRING		####
date.time.append <- function(str, sep = '_', date.format ="%Y_%m_%d_%H_%M_%S") {
stopifnot(is.character(str))
return(paste(str, format(Sys.time(), date.format), sep = sep))  
}

# 		TO USE THIS FUNCTION JUST ADD A STRING WITHIN THE PARENTHESESSS AS BELOW
# 		date.time.append("fileName")


####		Function to get correletions and p.values in a "long" data frame		####
corr.data = function(data) {
  
  # Get correlations
  cor.vals = cor(data)
  
  # Get p-values
  cor.p = cor.mtest(data, conf.level = 0.95)$p
  rownames(cor.p) = rownames(cor.vals)
  colnames(cor.p) = colnames(cor.vals)
  
  cbind(rowvars=rownames(cor.vals), data.frame(cor.vals)) %>% 
  	gather(colvars, corr, -rowvars) %>% 
  	left_join(cbind(rowvars=rownames(cor.p), data.frame(cor.p)) %>% 
  			  	gather(colvars, p.value, -rowvars))
}

##		END
```


```{r data prep, eval=FALSE, echo=FALSE}
####	THIS IS COMPLETED FOR THE DATA USED HERE AS OF April 23, 2020 		####
####		THIS DOESN’T NEED TO BE DONE FOR THE MOOD MANUSCRIPTS

##				NOTE			##
# Subject 248 WAKE TIME NEEDS TO BE CHANGED TO AM FROM PM
# THIS IS VERY VERY IMPORTANT

#		THIS SECTION PREPARED THE ORIGINAL DATA FOR SUBSEQUENT USE

#	This reads the files created by RedCap
# source('ImagingPsychometrics-BradPTConference_R_2020-03-16_1300.r')
# #		RENAME VARIABLE
# names(data)[names(data) == 'participant_id'] <- 'ID'
# # names(data)[names(data) == 'psqi_1']  <- 'psqi.bedtime'
# # names(data)[names(data) == 'psqi_1a.factor'] <- 'psqi.bt.sleep'
# # names(data)[names(data) == 'psqi_3'] <- 'psqi.waketime'
# # names(data)[names(data) == 'psqi_3a.factor'] <- 'psqi.wt.wake'
# # 
# #		WRITE NEW DATASET
# write_csv(data, "PT_data_13042020.csv",
# 		  na = "NA", append = FALSE,
# 		  col_names = TRUE, quote_escape = "double")

# 
# 


```


# DATA
Import data from GitHub
```{r Import-data, eval=TRUE, echo=TRUE, message=FALSE, comment = ""}
#		IMPORT DATA FROM GITHUB
data <- read.csv(url('https://raw.githubusercontent.com/BrainStormCenter/Manuscripts/master/Mood_DMN_2gps/behavioral_data_13042020.csv'), header = TRUE)
data <- as_tibble(data)

# 'https://raw.githubusercontent.com/BrainStormCenter/Manuscripts/Mood_DMN_2gps/behavioral_data_13042020.csv'), header = TRUE)
#https://raw.githubusercontent.com/BrainStormCenter/Manuscripts/master/Mood_DMN_2gps/behavioral_data_13042020.csv

# Mood_DMN_2gps/behavioral_data_13042020.csv

```

Import Subs list from GitHub
```{r Import_Subs, eval=TRUE, echo=TRUE, message=FALSE, comment = ""}
subs <- read.csv(url('https://raw.githubusercontent.com/BrainStormCenter/Manuscripts/master/Mood_DMN_2gps/SubjectList_2020_12_11_v1.csv'), header = TRUE)
subs <- as_tibble(subs)
subs <- subs %>% dplyr::select("ID") # has imaging data

```

```{r var_Names, eval=TRUE, echo=FALSE, message=FALSE, comment = ""}
#	LIST ALL THE VARIABLES IN THE DATA SET
# varNames <- colnames(dat0)
```

## Subset to subs with imaging data
```{r DataSubset, eval=TRUE, echo=TRUE, message=FALSE}
#	CREATE DATA SUBSET WITH ONLY SUBJECTS WITH IMAGING DATA
dat0 <- merge(data, subs)
dat0 <- as_tibble(dat0)

```


## 				FIND Var Names				##
<!-- ```{r var_Names, eval=TRUE, echo=FALSE, message=FALSE, comment = ""}
#	LIST ALL THE VARIABLES IN THE DATA SET
zvarNames <- tibble(colnames(dat0))

zVar <- as_tibble(zvarNames)


# m2 <- cbind(1, 1:4)
# colnames(m2, do.NULL = FALSE)
# colnames(m2) <- c("x","Y")
# rownames(m2) <- rownames(m2, do.NULL = FALSE, prefix = "Obs.")
# m2

``` -->


CHECK THAT THE DATA ARE THE CORRECT FORMAT/TYPE
```{r ---> Factor check}
#	CHECK WHICH VARIABLES ARE CODED AS FACTORS AND THEIR LEVELS
zdataFactors <- select_if(dat0, is.factor)
colnames(zdataFactors)
# levels(dataFactors$sex.fct)
# levels(dataFactors$painduration)

rm(dataFactors)

```


# CLEAN DATA
```{r Clean-data, eval=TRUE, echo=TRUE, message=FALSE, comment="", tidy=TRUE}
#		CLEANING AND PRESERVING ORIGINAL DATA

data %>% count(group)

##					Preserve data		##
dat1  <- dat0
dat1 %>% count(group)

###					CREATING FACTORS			####
dat1$group.factor = factor(dat1$group,levels=c("1","2","3"))
levels(dat1$group.factor)=c("HC","CLBP","FM", na.rm = TRUE)
dat1 %>% count(group.factor)

dat1$sex.factor = factor(dat1$sex, levels = c("1", "2"))
levels(dat1$sex.factor) = c("Male", "Female", na.rm = FALSE)
			
dat1$v1mood.factor = factor(dat1$visit1condition, levels = c("1", "2"))  
levels(dat1$v1mood.factor) = c("Pos1", "Neg1", na.rm = FALSE)

dat1$v2mood.factor = factor(dat1$visit2condition, levels = c("1", "2")) 
levels(dat1$v2mood.factor) = c("Pos2", "Neg2", na.rm = FALSE)

#			CHECK WHICH VARIABLES ARE CODED AS FACTORS AND THEIR LEVELS
zdataFactors <- select_if(dat1, is.factor)
colnames(zdataFactors)
rm(zdataFactors)

##			USED FOR FINDING ORIGINAL VARIABLES		##
# select(dat1, contains("mood"))
# select(dat1, contains("cond"))

# levels(dataFactors$sex.fct)
# levels(dataFactors$painduration)

###				CLEANING SPECIFIC VARIABLES			###
#				Clean BDI		##
# dat1  <- filter(dat1, group.factor != 0, dat1$bdi1 != "NA")
dat1 %>% count(group.factor)

##				REPLACE HC McGILL TOTAL "NA" WITH 0		##
dat1$mcgill_total  <- coalesce(dat1$mcgill_total, 0L)


##		CHANGE VARIABLE TYPE		##
dat1$ess_total <- as.numeric(dat1$ess_total)
dat1$bdi_total <- as.numeric(dat1$bdi_total)
dat1$mcgill_total <- as.numeric(dat1$mcgill_total)

##		REDUCE GROUPS TO JUST HC AND CLBP		##
dat1   <- filter(dat1, group.factor != "FM")

##		FINAL SUBJECT COUNT		##
dat1 %>% count(group.factor)

####				UNUSED COMMANDS				####
##				CLEAN ESS BY REMOVING "NA"		##
# dat1   <- filter(dat1, ess_total != "NA")

##						ISI					##
#		The Insomnia Severity Index score "isi_total" is already computed

#		Renaming a variable
# names(dat1)[names(dat1) == 'gp.fct'] <- 'group.factor'

# vNames <- colnames(dat0) 

##						END						##
```




## PSQI
* The global PSQI score is then calculated by totaling the seven component scores, providing an overall score ranging from 0 to 21, where lower scores denote a healthier sleep quality.   
* A PSQI Global score ≥ 5 is the clinical cutoff score (i.e., sleep problems)

```{r PSQI-Data, eval=TRUE, echo=TRUE, message=FALSE}
#		PSQI DATA
# gather psqi variables into separate data frame
dat.psqi <- dat1[,c(1,425,769,
					  grep("pittsburgh", colnames(dat1)),
					  grep("psqi", colnames(dat1)))]
#grep("timestamp", colnames(dat.raw))

# colnames(dat.psqi)
# label(dat.psqi)
# view(dat.psqi)

#	REORGANIZE VARIABLES
dat.psqi <- dat.psqi %>% select(1:7,43,everything()) 
dat.psqi <- dat.psqi %>% select(1:11,44,everything()) 
dat.psqi <- dat.psqi %>% select(1:14,45,everything()) 
dat.psqi <- dat.psqi %>% select(1:16,46,everything()) 
dat.psqi <- dat.psqi %>% select(1:18,47,everything())
dat.psqi <- dat.psqi %>% select(1:20,48,everything())
dat.psqi <- dat.psqi %>% select(1:22,49,everything())
dat.psqi <- dat.psqi %>% select(1:24,50,everything())
dat.psqi <- dat.psqi %>% select(1:26,51,everything())
dat.psqi <- dat.psqi %>% select(1:28,52,everything())
dat.psqi <- dat.psqi %>% select(1:30,53,everything())
dat.psqi <- dat.psqi %>% select(1:32,54,everything())
dat.psqi <- dat.psqi %>% select(1:35,55,everything())
dat.psqi <- dat.psqi %>% select(1:37,56,everything())
dat.psqi <- dat.psqi %>% select(1:39,57,everything())
dat.psqi <- dat.psqi %>% select(1:41,psqi_8b.factor,
								psqi_9, psqi_9.factor,
								everything())
dat.psqi <- dat.psqi %>% select(1:45,
								psqi_10.factor,
								psqi_10a, psqi_10a.factor,
								psqi_10b, psqi_10b.factor,
								psqi_10c, psqi_10c.factor,
								psqi_10d, psqi_10d.factor,
								psqi_10e, 
								psqi_10e1, psqi_10e1.factor,
								everything())

dat.psqi <- dat.psqi %>% select(1:2,group.factor,everything())


#### 			chr to num, eval=TRUE, echo=FALSE}			####
dat.psqi$psqi_2 <- as.numeric(dat.psqi$psqi_2)
dat.psqi$psqi_4 <- as.numeric(dat.psqi$psqi_4)
dat.psqi$psqi_5a <- as.numeric(dat.psqi$psqi_5a)
dat.psqi$psqi_5b <- as.numeric(dat.psqi$psqi_5b)
dat.psqi$psqi_5c <- as.numeric(dat.psqi$psqi_5c)
dat.psqi$psqi_5d <- as.numeric(dat.psqi$psqi_5d)
dat.psqi$psqi_5e <- as.numeric(dat.psqi$psqi_5e)
dat.psqi$psqi_5f <- as.numeric(dat.psqi$psqi_5f)
dat.psqi$psqi_5g <- as.numeric(dat.psqi$psqi_5g)
dat.psqi$psqi_5h <- as.numeric(dat.psqi$psqi_5h)
dat.psqi$psqi_5i <- as.numeric(dat.psqi$psqi_5i)
dat.psqi$psqi_5othera <- as.numeric(dat.psqi$psqi_5othera)
dat.psqi$psqi_7 <- as.numeric(dat.psqi$psqi_7)
dat.psqi$psqi_8a <- as.numeric(dat.psqi$psqi_8a)
dat.psqi$psqi_9 <- as.numeric(dat.psqi$psqi_9)
dat.psqi$psqi_component1 <- as.numeric(dat.psqi$psqi_component1)


#		REPLACE "NA" WITH 0
dat.psqi$psqi_5othera <- dat.psqi$psqi_5othera %>% replace_na(0)


####			PSQI TIB SANITY CHECK			####
# max(dat1$TIB)

# colnames(dat1)
# da# z <- data[which(dat.psqi$TIB > 19, ) ]
```


```{r TIB, eval=TRUE, echo=TRUE}
#		Estimate time in bed (TIB)

dat.psqi$bedtime  <- dat.psqi$psqi_1
dat.psqi$bt.sleep <- dat.psqi$psqi_1a.factor
dat.psqi$waketime <- dat.psqi$psqi_3
dat.psqi$wt.wake <- dat.psqi$psqi_3a.factor

#		FOR FORUM HELP VERSION #1
#		GOING TO SLEEP AND WAKING UP ON THE SAME DAY RESULTS IN 24+ HOURS
dat.psqi <- dat.psqi %>%
	mutate_all(.funs = as.character) %>%
	mutate_at(.vars = c("bt.sleep", "wt.wake"),
			  .funs = ~ gsub(pattern = ".",
			  			   replacement = "",
			  			   x = .x,
			  			   fixed = TRUE)) %>%
	mutate(Sleep = as.POSIXct(x = paste(bedtime, bt.sleep),
							  format = "%I:%M %p"),
		   Wake = as.POSIXct(x = paste(waketime, wt.wake),
		   				  format = "%I:%M %p") +
		   	as.difftime(tim = 1, units = "days"),
		   `Time in bed` = Wake - Sleep) # TIB version 1

#		CRUDE FIX FOR THE 24+ HOUR ISSUE
dat.psqi$TIB  <- as.numeric(dat.psqi$`Time in bed`)   # TIB version 2

# round(dat.psqi$TIB  <- if_else(dat.psqi$TIB < 24,
# 							   dat.psqi$TIB,
# 							   dat.psqi$TIB - 24), 2)

# 
# dat.psqi$TIB2  <- if_else(dat.psqi$TIB < 24,
# 							   dat.psqi$TIB,
# 							   dat.psqi$TIB - 24) # TIB version 3
# 
# 


# ###			Second version from forum		###
# dat.psqi <- dat.psqi %>%
#   mutate(Sleep = if_else(
#   	bt.sleep == "PM", true = as.POSIXct(x = paste(bedtime, bt.sleep), 
#   										format = "%I:%M %p"), # time in current date
#   	false = as.POSIXct(x = paste(bedtime, bt.sleep), 
#   					   format = "%I:%M %p") + 
#   		as.difftime(tim = 1, units = "days")), # next day for times at/after midnight
#          Wake = as.POSIXct(x = paste(waketime, wt.wake),
#          				  format = "%I:%M %p") +
#   		as.difftime(tim = 1, units = "days"), # time in current date plus one day, equivalently time in next day
#   	`Time Difference` = difftime(time1 = Wake,
#   								 time2 = Sleep,
#   								 units = "hours")) %>%  # difference of the two times, guaranteed to be in [0, 24)
# 	print(width = Inf) # TIB version 4
# 
# 
# dat.psqi$TIB <- dat.psqi$`Time Difference`
# 
# dat.psqi <- dat.psqi %>% relocate(`Time Difference`, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(`TIB`, .after = last_col())
# dat.psqi <- dat.psqi %>% relocate(`Time in bed`, .after = last_col())
# dat.psqi <- dat.psqi %>% relocate(`TIB2`, .after = last_col())





# write.csv(dat.psqi, "PSQI_rawData_April2020_v1.csv", row.names = FALSE)

# currentDate <- format(Sys.time(), "%F_%H-%M")
# write_csv(dat.psqi,
# 		  paste("PSQI_rawData_",currentDate,".csv",sep=""),
# 		  na = "NA",
# 		  col_names = TRUE, quote_escape = "double")


# colnames(dat.psqi)

```


```{r COMP-1, eval=TRUE, echo=FALSE}
#		COMPONENT 1 = QUESTION 9
dat.psqi$psqi_comp1raw <- as.numeric(dat.psqi$psqi_component1)
dat.psqi$psqi_Comp1 <- as.numeric(dat.psqi$psqi_component1)

#		SCORE QUESTION 1
# Component 1: Subjective sleep quality—question 9
# Response, Component Score to Q9 
# Very good, 0
# Fairly good, 1
# Fairly bad, 2
# Very bad, 3

dat.psqi <- dat.psqi %>% relocate(psqi_comp1raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp1, .after = last_col())
# colnames(dat.psqi)
```


```{r COMP-2, eval=TRUE, echo=FALSE}
# Component 2: Sleep latency—questions 2 and 5a

dat.psqi$Q2 <- as.numeric(dat.psqi$psqi_2)
dat.psqi$Q5a <- as.numeric(dat.psqi$psqi_5a)

#		SCALE Q2
dat.psqi  <- dat.psqi %>%
	mutate(
		Q2score1 = case_when(
			Q2 <= 15 ~ 0,
			Q2 >= 16 & Q2 <= 30 ~ 1,
			Q2 >= 31 & Q2 <= 60 ~ 2,
			Q2 > 60 ~ 3,
			TRUE ~ as.numeric(Q2)
		)
	)
#		SCALE Q5
dat.psqi <- dat.psqi %>% 
	mutate(
		Q5aScore1 = case_when(
			Q5a == 1 ~ 0,
			Q5a == 2 ~ 1,
			Q5a == 3 ~ 2,
			Q5a == 4 ~ 3,
			TRUE ~ as.numeric(Q5a)
		)
	)

#		CALC COMP-2 RAW AND SCALED SCORES
dat.psqi  <- dat.psqi %>%
	rowwise() %>%
	mutate(
		psqi_comp2raw = sum(c(Q2, Q5a), na.rm = TRUE),
		Q2and5 = sum(c(Q2score1, Q5aScore1), na.rm = TRUE)
	) %>%
	ungroup()


	#		RESCALE THE COMP 2 SCALED SCORES
dat.psqi <- dat.psqi %>% 
	mutate(
		psqi_Comp2 = case_when(
			Q2and5 == 0 ~ 0,
			Q2and5 >= 1 & Q2and5 <= 2 ~ 1,
			Q2and5 >= 3 & Q2and5 <= 4 ~ 2,
			Q2and5 >= 5 & Q2and5 <= 6 ~ 3,
			TRUE ~ as.numeric(Q2and5)
		)
	)
dat.psqi <- dat.psqi %>% relocate(psqi_comp1raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp2raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp1, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp2, .after = last_col())
# colnames(dat.psqi)
```


```{r COMP-3, eval=TRUE, echo=FALSE}
# Component 3: Sleep duration—question 4

dat.psqi$Q4 <- as.numeric(dat.psqi$psqi_4)
dat.psqi$psqi_comp3raw <- as.numeric(dat.psqi$psqi_4)

#		COMP 3 SCALED SCORE
dat.psqi  <- dat.psqi %>%
	mutate(
		psqi_Comp3 = case_when(
			Q4 > 7 ~ 0,
			Q4 >= 6 & Q4 <= 7 ~ 1,
			Q4 >= 5 & Q4 < 6 ~ 2,
			Q4 < 5 ~ 3,
			TRUE ~ as.numeric(Q4)
		)
	)

dat.psqi <- dat.psqi %>% relocate(Q4, .before = psqi_Comp1)
# colnames(dat.psqi)
```


```{r COMP-4, eval=TRUE, echo=FALSE}
# Component 4: Sleep efficiency—questions 1, 3, and 4
# Sleep efficiency = (# hours slept/# hours in bed) X 100% 
#	= (Q4 / TIB) * 100
# hours slept—question 4
# hours in bed—calculated from responses to questions 1 and 3
# 	Sleep efficiency, Component score 
# 		> 85%, 0	
# 		75-84%, 1
# 		65-74%, 2
# 		< 65%, 3

dat.psqi$psqi_comp4raw <- (dat.psqi$Q4 / dat.psqi$TIB) * 100
dat.psqi$SE <- (dat.psqi$Q4 / dat.psqi$TIB) * 100

dat.psqi  <- dat.psqi %>%
	mutate(
		psqi_Comp4 = case_when(
			SE >= 85 ~ 0,
			SE >= 75 & SE < 85 ~ 1,
			SE >= 65 & SE < 75 ~ 2,
			SE < 65 ~ 3,
			TRUE ~ as.numeric(SE)
		)
	)

dat.psqi <- dat.psqi %>% relocate(SE, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_comp1raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp2raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp3raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp4raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp1, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp2, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp3, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp4, .after = last_col())
# colnames(dat.psqi)
```


```{r COMP-5, eval=TRUE, echo=FALSE}
# Sum of 5b to 5j scores, Component 5 score
# 0, 0
# 1-9, 1
# 10-18, 2 
# 19-27, 3


###		NEED TO DO THIS TWICE FOR SOME REASON	####
dat.psqi$psqi_2 <- as.numeric(dat.psqi$psqi_2)
dat.psqi$psqi_4 <- as.numeric(dat.psqi$psqi_4)
dat.psqi$psqi_5a <- as.numeric(dat.psqi$psqi_5a)
dat.psqi$psqi_5b <- as.numeric(dat.psqi$psqi_5b)
dat.psqi$psqi_5c <- as.numeric(dat.psqi$psqi_5c)
dat.psqi$psqi_5d <- as.numeric(dat.psqi$psqi_5d)
dat.psqi$psqi_5e <- as.numeric(dat.psqi$psqi_5e)
dat.psqi$psqi_5f <- as.numeric(dat.psqi$psqi_5f)
dat.psqi$psqi_5g <- as.numeric(dat.psqi$psqi_5g)
dat.psqi$psqi_5h <- as.numeric(dat.psqi$psqi_5h)
dat.psqi$psqi_5i <- as.numeric(dat.psqi$psqi_5i)
dat.psqi$psqi_5othera <- as.numeric(dat.psqi$psqi_5othera)
dat.psqi$psqi_7 <- as.numeric(dat.psqi$psqi_7)
dat.psqi$psqi_8a <- as.numeric(dat.psqi$psqi_8a)
dat.psqi$psqi_9 <- as.numeric(dat.psqi$psqi_9)
dat.psqi$psqi_component1 <- as.numeric(dat.psqi$psqi_component1)

dat.psqi$psqi_5j <- dat.psqi$psqi_5othera # copy variable

#		REARRANGE COLUMNS - AGAIN
dat.psqi <- dat.psqi %>% relocate(psqi_5othera, .before = psqi_5b)
dat.psqi <- dat.psqi %>% relocate(psqi_5b, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5c, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5d, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5e, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5f, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5g, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5h, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5i, .before = psqi_Comp1)
dat.psqi <- dat.psqi %>% relocate(psqi_5j, .before = psqi_Comp1)


#		RESCORE THE RESPONSES - ORIG = 1-4; NEW = 0-3
#		THIS REPLACES THE VALUES IN THE ORIGINAL VARIABLES
# dat.psqi <- dat.psqi %>% 
# 	mutate_at(vars(matches("psqi_5[b-i]$")), ~ . - 1)

#		RESCORING THE LONG WAY
dat.psqi$Q5b <- dat.psqi$psqi_5b -1
dat.psqi$Q5c <- dat.psqi$psqi_5c -1
dat.psqi$Q5d <- dat.psqi$psqi_5d -1
dat.psqi$Q5e <- dat.psqi$psqi_5e -1
dat.psqi$Q5f <- dat.psqi$psqi_5f -1
dat.psqi$Q5g <- dat.psqi$psqi_5g -1
dat.psqi$Q5h <- dat.psqi$psqi_5h -1
dat.psqi$Q5i <- dat.psqi$psqi_5i -1
dat.psqi$Q5j <- dat.psqi$psqi_5j 

#		SUMMING THE SCORES
dat.psqi  <- dat.psqi %>%
	rowwise() %>%
	mutate(
		psqi_comp5raw = sum(c(Q5b, Q5c, Q5d, Q5e, Q5f, 
							  Q5g, Q5h, Q5i, Q5j), na.rm = TRUE),
		Q5s = sum(c(Q5b, Q5c, Q5d, Q5e, Q5f, Q5g, Q5h, Q5i, Q5j), na.rm = TRUE)
	) %>%
	ungroup()


# Sum of 5b to 5j scores, Component 5 score
# 0, 0
# 1-9, 1
# 10-18, 2 
# 19-27, 3
#		CONVERTING TO COMPONENT SCORE
dat.psqi <- dat.psqi %>% 
	mutate(
		psqi_Comp5 = case_when(
			Q5s < 1 ~ 0,
			Q5s >= 1 & Q5s <=9 ~ 1,
			Q5s >= 10 & Q5s <=18 ~ 1,
			Q5s >= 19 & Q5s <=27 ~ 1,
			TRUE ~ as.numeric(Q5s)
		)
	)


#		ORGANIZING COLUMNS
dat.psqi <- dat.psqi %>% relocate(psqi_comp1raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp2raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp3raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp4raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp5raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp1, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp2, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp3, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp4, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp5, .after = last_col())


# colnames(dat.psqi)

```


```{r COMP-6, eval=TRUE, echo=FALSE}
# Component 6: Use of sleep medication—question 6
# Response to Q6, Component 6 score
# Not during past month, 0
# Less than once a week, 1 
# Once or twice a week, 2
# Three or more times a week, 3

dat.psqi$psqi_comp6raw <- as.numeric(dat.psqi$psqi_6)
dat.psqi$psqi_Comp6 <- as.numeric(dat.psqi$psqi_6)
# colnames(dat.psqi)

```


```{r COMP-7, eval=TRUE, echo=FALSE}
# 	Component 7: SUM Daytime dysfunction—questions 7 and 8
# Sum of Q7 and Q8 subscores, COMPONENT SCORE 
# 0,0
# 1-2 1 
# 3-4 2 
# 5-6 3

#		SUM QUESTIONS 7 AND 8a
dat.psqi  <- dat.psqi %>%
	rowwise() %>%
	mutate(
		psqi_comp7raw = sum(c(psqi_7, psqi_8a), na.rm = TRUE),
		Q7and8a = sum(c(psqi_7, psqi_8a), na.rm = TRUE)
	) %>%
	ungroup()

#		SCORE COMPONENT 7
dat.psqi  <- dat.psqi %>%
	mutate(
		psqi_Comp7 = case_when(
			Q7and8a > 1 ~ 0,
			Q7and8a >= 1 & Q7and8a <= 2 ~ 1,
			Q7and8a >= 3 & Q7and8a <= 4 ~ 2,
			Q7and8a >= 5 & Q7and8a <= 6 ~ 3,
			TRUE ~ as.numeric(Q7and8a)
		)
	)


#		ORGANIZING COLUMNS
dat.psqi <- dat.psqi %>% relocate(psqi_comp1raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp2raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp3raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp4raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp5raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp6raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_comp7raw, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp1, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp2, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp3, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp4, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp5, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp6, .after = last_col())
dat.psqi <- dat.psqi %>% relocate(psqi_Comp7, .after = last_col())

```


```{r GLOBAL-Score, eval=TRUE, echo=FALSE}
# Global PSQI Score: Sum of seven component scores:

dat.psqi  <- dat.psqi %>%
	rowwise() %>%
	mutate(
		psqi_Globalraw = sum(c(psqi_comp1raw, psqi_comp2raw, psqi_comp3raw,
							psqi_comp4raw, psqi_comp5raw, psqi_comp6raw,
							psqi_comp7raw), na.rm = TRUE),
		psqi_Global = sum(c(psqi_Comp1, psqi_Comp2, psqi_Comp3,
							psqi_Comp4, psqi_Comp5, psqi_Comp6,
							psqi_Comp7), na.rm = TRUE)
	) %>%
	ungroup()


# colnames(dat.psqi)

```


```{r RENAME COMPS, eval=TRUE, echo=FALSE}
#		RENAME THE PSQI COMPONENTS
names(dat.psqi)[names(dat.psqi) == 'psqi_comp1raw'] <- 'slpQualraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp2raw'] <- 'slpLatraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp3raw'] <- 'slpDurraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp4raw'] <- 'slpEffraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp5raw'] <- 'slpDistraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp6raw'] <- 'slpMedsraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_comp7raw'] <- 'slpDayFcnraw'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp1'] <- 'slpQual'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp2'] <- 'slpLat'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp3'] <- 'slpDur'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp4'] <- 'slpEff'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp5'] <- 'slpDist'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp6'] <- 'slpMeds'
names(dat.psqi)[names(dat.psqi) == 'psqi_Comp7'] <- 'slpDayFcn'

# colnames(dat.psqi)

# currentDate <- format(Sys.time(), "%F_%H-%M")
# write_csv(dat.psqi,
# 		  paste("PSQI_scored_",currentDate,".csv",sep=""),
# 		  na = "NA",
# 		  col_names = TRUE, quote_escape = "double")

```


```{r REINTEGRATE, eval=TRUE, echo=FALSE}
#		COMBINING 2 DATASETS
#		MERGE PSQI DATA BACK INTO MAIN DATASET

#		CREATING SMALL PSQI DATASET
psqiSM  <- dat.psqi %>% dplyr::select("ID","TIB",
									  "slpQual", "slpLat", 
									  "slpDur", "slpEff", 
									  "slpDist", "slpMeds",
									  "slpDayFcn", "psqi_Global",
									  "slpQualraw", "slpLatraw", 
									  "slpDurraw", "slpEffraw", 
									  "slpDistraw", "slpMedsraw",
									  "slpDayFcnraw", "psqi_Globalraw")
#		MERGE BACK INTO MAIN DATASET
dat1 <- merge(dat1, psqiSM, by = "ID")

# colnames(dat1)

```

* The PSQI data has been updated, processed, clean and scored  

* **NOTE:** I need to add a section that discusses the PSQI cutoff.
Anything over "5" is considered significant.

## INITIAL DATA SETS
Create a small dataset (dat.sm) that includes only the variables of interest.
```{r Primary-datasets, eval=TRUE, echo=FALSE, comment=""}
#		CREATING SMALL DATASETS

# datSM1  <- dat1 %>% dplyr::select("ID","group.factor","ess_total", "bdi_total", "mcgill_total")
dat.sm  <- dat1 %>% dplyr::select("group.factor",
								  "slpQual", "slpLat", 
								  "slpDur", "slpEff", 
								  "slpDist", "slpMeds",
								  "slpDayFcn", "psqi_Global",
								  "slpQualraw", "slpLatraw", 
								  "slpDurraw", "slpEffraw", 
								  "slpDistraw", "slpMedsraw",
								  "slpDayFcnraw", "psqi_Globalraw",
								  "ess_total", "isi_total",
								  "bdi_total", "mcgill_total", 
								  "TIB")

# dat.bar1.orig <- dat1 %>% dplyr::select("ID","group.factor",
# 								  "slpQual", "slpLat", 
# 								  "slpDur", "slpEff", 
# 								  "slpDist", "slpMeds",
# 								  "slpDayFcn", "psqi_Global",
# 								  "ess_total", "isi_total",
# 								  "bdi_total", "mcgill_total", 
# 								  "TIB")

dat.bar2.orig <- dat1 %>% dplyr::select("ID","group.factor",
										"slpQualraw", "slpLatraw", 
										"slpDurraw", "slpEffraw", 
										"slpDistraw", "slpMedsraw",
										"slpDayFcnraw", "psqi_Globalraw",
										"ess_total", "isi_total",
										"bdi_total", "mcgill_total", 
										"TIB")

dat.HC <- dat.sm %>%
	filter(group.factor == "HC")
dat.FM <- dat.sm %>%
	filter(group.factor == "FM")
dat.CLBP <- dat.sm %>%
	filter(group.factor == "CLBP")
dat.pain <- dat.sm %>%
	filter(group.factor == "CLBP" | group.factor == "FM")



# smallData <- paste("dat.sm2_",currentDate,".csv",sep="") 
# write_csv(dat.sm, smallData,
# 		  na = "NA", append = FALSE,
# 		  col_names = TRUE, quote_escape = "double")


#		TO RECREATE A DATASET
# dput(head(dat.time, 20))
# dput(datSM1)
#		NOT ALL SUBJECTS HAVE COMPLETE DATA
#		DONE AS OF March 31, 2020
```


## VARIANCE CHECK
Which variable(s) in the dat.sm data has potential issues with variances?

```{r QA-DATA, eval=TRUE, echo=TRUE, comment=""}
# dat.sm.smry <- by(dat.sm, dat.sm$group.factor, summary, na.rm = TRUE)
# 
# summarise(dat.sm)

#		LOOKING AT VARIANCE AMONG VARIABLES

nearZeroVar(dat.sm,
			uniqueCut = 2,
			names = TRUE)

```


```{r Exploring-data, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}
#-EXAMINE DATA
##-Reports - skipped for now
####				EXPLORING DATA WITH THE DATAEXPLORER PACKAGE
# library(DataExplorer)
# create_report(dat.isi)

```


# SAMPLE DESCRIPTIVES
## Group by sex for overall sample.
```{r Demographics, eval=FALSE, echo=TRUE}
#		GROUP BY SEX INFORMATION
group_by_sex <- dat1 %>%
	group_by(group.factor, sex.factor) %>%
	tally()

names(group_by_sex)[names(group_by_sex) == 'group.factor'] <- 'Group'
names(group_by_sex)[names(group_by_sex) == 'sex.factor'] <- 'Sex'

gpsex1 <- spread(group_by_sex, Sex, n) %>% 
	adorn_totals(c("row", "col"))

gpsex1 %>% 
	kable(align = "c", padding = 4, caption = "Entire Sample") %>% 
	kable_styling(c("striped", "bordered"), full_width = F) %>% 
	add_header_above(c(" ", "Sex" = 2, "")) %>%
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	row_spec(4, bold = T, background = "lightgrey") %>% 
	column_spec(4, bold = T, background = "lightgray")

#		END		#

```


## Group by age for overall sample.
```{r Gp_by_age, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}
newdf <- df %>% filter(party %in% c('R','D')) %>%
  group_by(termstart,party) %>% summarise(MeanAge=mean(age,na.rm=T)) %>%
  pivot_wider(names_from = party,values_from=MeanAge)

newdf <- dat1 %>% filter(group.factor %in% c('HC','CLBP', 'FM')) %>%
	group_by(group.factor) %>%
	summarise(MeanAge=mean(age_visit_1,na.rm=T), 
			  ageSD=sd(age_visit_1, na.rm = T)) 


#%>%
	pivot_longer(newdf,
				 group.factor,
				 names_from = group.factor,values_from=MeanAge)
#	pivot_wider(names_from = group.factor,values_from=MeanAge)
	
```


## t-test Age 2 groups
```{r ttest_Age, eval=TRUE, echo=FALSE, message=FALSE, comment = ""}

##		FINAL SUBJECT COUNT		##
dat1 %>% count(group.factor)

age.dat   <- filter(dat1, group.factor != "FM")

##		FINAL SUBJECT COUNT		##
age.dat %>% count(group.factor)

attach(age.dat)
boxplot(age.dat$age_visit_1 ~ age.dat$group)

# Ho: mean age of HC = CLBP
# two-sided test
# assume non-equal variances

ageGroup.dat <- t.test(age.dat$age_visit_1 ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

# ageEd.dat <- t.test(age.dat$education ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

ageGroup.dat

	
```


## MEAN AGE STUFF
```{r AgeMeans-SDs, eval=TRUE, echo=TRUE, message=FALSE, comment = ""}
means.age <- dat1 %>% dplyr::select("group.factor", "age_visit_1") 

means.age  <- filter(means.age, group.factor != TRUE)

meansAge.stats <- describeBy(means.age,
							group = "group.factor",
							interp = FALSE,
							skew = FALSE,
							ranges = FALSE,
							fast = NULL)

meansAge.stats 

# means.stats <- filter(means.stats,  group1 !="TRUE")

# means.stats99
# 
# means.stats99 %>% kable(align = "c", caption = "test") %>% 
# kable_styling(c("striped", "bordered"), full_width = F) %>% 
# 	# add_header_above(c(" ", "Sex" = 2, "")) %>%
# 	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
# 	row_spec(4, bold = T, background = "lightgrey")# %>% 
# 	# column_spec(4, bold = T, background = "lightgray")

	
	
```



Means and SDs for each group.
```{r Means-SDs, eval=TRUE, echo=TRUE, message=FALSE, comment = ""}
means.data <- dat1 %>% dplyr::select("group.factor",
                       "slpQual", "slpLat", 
                       "slpDur", "slpEff", 
                       "slpDayFcn", "psqi_Global",
                       "ess_total", "bdi_total", 
                       "mcgill_total") 

means.data   <- filter(means.data, group.factor != TRUE)

means.stats <- describeBy(means.data,
							group = "group.factor",
							interp = FALSE,
							skew = FALSE,
							ranges = FALSE,
							fast = NULL)

means.stats 

# means.stats <- filter(means.stats,  group1 !="TRUE")

# means.stats99
# 
# means.stats99 %>% kable(align = "c", caption = "test") %>% 
# kable_styling(c("striped", "bordered"), full_width = F) %>% 
# 	# add_header_above(c(" ", "Sex" = 2, "")) %>%
# 	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
# 	row_spec(4, bold = T, background = "lightgrey")# %>% 
# 	# column_spec(4, bold = T, background = "lightgray")

	
	
```


#PLOTS

## CORR PLOTS

```{r HC-Group, eval=TRUE, echo=FALSE, message=FALSE}
######		HC GROUP			####
dat.HC2 <- dat.HC %>% select(!"group.factor", -isi_total)
dat.HC2 <- dat.HC2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.HC2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "HC group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r CLBP-Group, eval=TRUE, echo=FALSE, message=FALSE}
######		CLBP GROUP			####
dat.CLBP2 <- dat.CLBP %>% select(!"group.factor", -isi_total)
dat.CLBP2 <- dat.CLBP2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.CLBP2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "CLBP group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r FM-Group, eval=TRUE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.FM2 <- dat.FM %>% select(!"group.factor", -isi_total)
dat.FM2 <- dat.FM2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.FM2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "FM group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r Pain-Groups, eval=TRUE, echo=FALSE, message=FALSE}
######		PAIN GROUPS			####
dat.pain2 <- dat.pain %>% select(!"group.factor", -isi_total)
dat.pain2 <- dat.pain2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.pain2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "Both pain groups",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r CLBP-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.CLBP2 <- dat.CLBP %>% select(!"group.factor", -TIB)
dat.CLBP2 <- dat.CLBP2 %>% select(!"slpDist")

####		Breaking down the plot		####

corr.data(dat.CLBP2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 1.5, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=1.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "CLBP pain group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +

```


```{r HC-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.HC2 <- dat.HC %>% select(!"group.factor", -TIB)
dat.HC2 <- dat.HC2 %>% select(!"slpDist")

####		Breaking down the plot		####

corr.data(dat.HC2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 1.5, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=1.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "Healthy control group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
	# theme_classic() +
	# theme_cleveland() +

```


The end of corr plots

## BAR PLOTS
```{r BARS-1, eval=TRUE, echo=FALSE, message=FALSE}
dat.bar1.orig  <- dat1 %>% dplyr::select("ID","group.factor",
										 "slpQual", "slpLat", 
										 "slpDur", "slpEff", 
										 "slpDayFcn", "psqi_Global",
										 "ess_total", "bdi_total", 
										 "mcgill_total")

dat.bar1.orig$ID <- factor(dat.bar1.orig$ID) # ID must be a factor
names(dat.bar1.orig)[names(dat.bar1.orig)=="group.factor"] <- "group"


####			BAR CHART DATA NEED TO BE IN LONG FORMAT		####

#		Plot all the data at once
dat.bar0 <- dat.bar1.orig

#	select data for 1st bar chart = BDI, ESS, McGill
dat.bar1a <- select(dat.bar1.orig, ID, group, 
					slpDayFcn, slpEff, slpDur,
					slpQual, slpLat)

#	select data for 2nd bar chart
dat.bar1b <- select(dat.bar1.orig, ID, group, 
				   ess_total, psqi_Global, bdi_total)

#	select data for 3rd bar chart
dat.bar1c <- select(dat.bar1.orig, ID, group, 
					mcgill_total)

#	select data for 3rd bar chart
dat.bar1d <- select(dat.bar1.orig, ID, group, 
					mcgill_total, psqi_Global)




# str(dat.bar)

#		Convert to long format
bar0.melt <- melt(dat.bar0, id.vars = c("ID", "group")) 
bar1a.melt <- melt(dat.bar1a, id.vars = c("ID", "group")) 
bar1b.melt <- melt(dat.bar1b, id.vars = c("ID", "group"))
bar1c.melt <- melt(dat.bar1c, id.vars = c("ID", "group"))
bar1d.melt <- melt(dat.bar1d, id.vars = c("ID", "group"))

# head(bar1a.melt)

#		Rename "value"
names(bar0.melt)[names(bar0.melt)=="value"] <- "score"
names(bar1a.melt)[names(bar1a.melt)=="value"] <- "score"
names(bar1b.melt)[names(bar1b.melt)=="value"] <- "score"
names(bar1c.melt)[names(bar1c.melt)=="value"] <- "score"
names(bar1d.melt)[names(bar1d.melt)=="value"] <- "score"


#		Calculate means and sem
bar0.means <- ddply(bar0.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sd = sd(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1a.means <- ddply(bar1a.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)


bar1b.means <- ddply(bar1b.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1c.means <- ddply(bar1c.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1d.means <- ddply(bar1d.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)


#		PLOT THE LONG DATA
ggplot(bar0.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,40)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	# scale_x_discrete(limits = vlevels1a) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons of all vars") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) 


ggplot(bar1a.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,2.5)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons of psqi vars") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) 


ggplot(bar1b.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	# coord_cartesian(ylim = c(0,3)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons")

ggplot(bar1c.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,40)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "McGill pain questionnaire")

# ggplot(bar1d.means, aes(x = variable, y = mean, fill = group )) +
# 	geom_bar(position = position_dodge(.9), colour = "black", 
# 			 stat = "identity") +
# 	geom_errorbar(position = position_dodge(.9), width = .25,
# 				  aes(ymin = mean - sem, ymax = mean + sem)) +
# 	# coord_cartesian(ylim = c(0,40)) +
# 	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
# 	scale_y_continuous(breaks = waiver()) +
# 	geom_hline(yintercept = 0)


```


```{r BARPLOT-test, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}

#		VISUALIZE THE GROUP DIFFERENCES	WITH SIG LEVELS		#
# Bar plot of mean +/-se
ggbarplot(ToothGrowth, x = "dose", y = "len", add = "mean_se")+
  stat_compare_means() +                                         # Global p-value
  stat_compare_means(ref.group = "0.5", label = "p.signif",
                     label.y = c(22, 29))                   # compare to ref.group

# Line plot of mean +/-se
ggline(ToothGrowth, x = "dose", y = "len", add = "mean_se")+
  stat_compare_means() +                                         # Global p-value
  stat_compare_means(ref.group = "0.5", label = "p.signif",
                     label.y = c(22, 29))     

# _________________________________________#
#		EXAMPLE		#

zdat <- data.frame(Group = c("S1", "S1", "S2", "S2"),
              Sub   = c("A", "B", "A", "B"),
              Value = c(3,5,7,8))  

ggplot(zdat, aes(Group, Value)) +
	geom_bar(aes(fill = Sub), stat="identity", 
			 position="dodge", width=.5) +
	geom_signif(stat="identity",
				data=data.frame(x=c(0.875, 1.875),
								xend=c(1.125, 2.125),
								y=c(5.8, 8.5), 
								annotation=c("**", "NS")),
				aes(x=x,xend=xend, y=y, yend=y,
					annotation=annotation)) #+
	geom_signif(comparisons=list(c("S1", "S2")),
				annotations="***",
				y_position = 9.3, 
				tip_length = 0, vjust=0.4) 
# +
	# scale_fill_manual(values = c("grey80", "grey20"))

#___________________________________________#
library(ggplot2)
library(ggpval)
data("PlantGrowth")
plt <- ggplot(PlantGrowth, aes(group, weight)) +
  geom_boxplot()
add_pval(plt, pairs = list(c(1, 3)), test='wilcox.test')
#_________________________________________

ggplot(bar1a.means, aes(variable, mean)) +
	geom_bar(aes(fill = group),
			 stat = "identity",
			 position = "dodge", 
			 width = .5) +
	geom_signif(stat = "identity",
				data=data.frame(x=c(0.875, 1.875),
								xend=c(1.125, 2.125),
								y=c(2.5, 3.5), 
								annotation=c("***", "bob")),
				aes(x=x,xend=xend, y=y, yend=y,
					annotation=annotation))

```



## BOX PLOTS
```{r Box-plots, eval=FALSE, echo=FALSE, message=FALSE}
####		PSQI BOXPLOT		####
head(dat.bar1a)
head(bar1a.means)
ggplot(bar1a.means, aes(x = group, y = mean )) +
	geom_boxplot() +
	geom_signif(comparisons = list(c("HC", "CLBP"),
								   c("HC", "FM"),
								   c("CLBP", "FM")),
				 # y_position = c(30, 40, 25),
				map_signif_level=function(p)sprintf("p = %.2g", p))



```


```{r BOXPLOT-test, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}
# PERFORMING TEST
compare_means(mcgill_total ~ group.factor, data = dat1,
			  ref.group = ".all.", method = "t.test")


#		VISUALIZE THE GROUP DIFFERENCES			#
# 		Pairwise comparison of all agains the grand mean (I think)
ggboxplot(dat1, x = "group.factor",
		  y = "mcgill_total",
		  color = "group.factor",
		  add = "jitter",
		  legend = "none") +
	rotate_x_text(angle = 45) +
	geom_hline(yintercept = mean(dat1$mcgill_total),
			   linetype = 2) + # add horizontal line at base mean
	stat_compare_means(method = "anova", label.y = 80) +
	stat_compare_means(label = "p.signif",
					   method = "t.test",
					   ref.group = ".all.")  

#		VISUALIZE GROUP DIFS WITH SIG LEVELS IN PLOT
gp_comparisons = list(c("HC", "CLBP"),
					  c("CLBP", "FM"),
					  c("HC", "FM"))

ggboxplot(dat1,
		  x = "group.factor",
		  y = "mcgill_total",
		  color =  "group.factor",
		  palette = "jco") +
	stat_compare_means(comparisons = gp_comparisons,
					   label.y = c(45, 55, 65)) +
	stat_compare_means(label.y = 80)


##			END			##
```


# ANOVA (Main effect of group)
```{r ANOVA-scaleddata, eval=TRUE, echo=TRUE, message=FALSE}
# construct anova model for each column of dat1[, my_outcome_variables]
model_summaries <- dat1[,c("age_visit_1","slpQual", "slpLat", "slpDur",
						   "slpEff", "slpDist","slpMeds",
						   "slpDayFcn", "psqi_Global","ess_total",
						   "isi_total", "bdi_total", "mcgill_total",
						   "TIB")] %>%
  purrr::map(~ aov(.x ~ group.factor, data = dat1))  %>%
  # append the TukeyHSD CI estimates
  purrr::map(function(x) {
    list(
      model = x,
      tukey = TukeyHSD(x)
    )
  })

####		THIS RETURNS THE RESULTS OF THE OVERALL ANOVA	####
GetModels <- function(l) l$model
Models <- purrr::map(model_summaries, GetModels) %>% 
  purrr::map_dfr(broom::tidy, .id = "Name")
# head(Models)

#		
Models2 <- filter(Models,  term !="Residuals")
Models2 <- Models2 %>% 
	dplyr::select("Name" , "p.value")


####			ANOVA TABLE MADE WITH KABLE			####
Models2 %>%
	mutate(p.value = 
		   	cell_spec(
		   		(formatC(x = p.value, 
		   				 digits=3, width = 3, 
		   				 format='g', flag = "-", drop0trailing = TRUE, 
		   				 preserve.width = "common")), "html",
		   		color = ifelse(p.value <= 0.054, 
		   					   yes="red", no="blue"), escape = F)
	) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec(
			(formatC(x,digits=3, width=3, 
					 format="f", flag="-", drop0trailing = FALSE)),
			"html")}
	) %>%
	kable("html", escape = FALSE, align = "l", padding = 4,
		  caption = "ANOVA full model") %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant main effect for group (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" )

##		END		##
```


```{r ANOVA-rawdata, eval=FALSE, echo=TRUE, message=FALSE}
#		USING PSQI RAW COMPONENT SCORES
# construct anova model for each column of dat1[, my_outcome_variables]
model_summary_raw <- dat1[,c("age_visit_1", "slpQualraw", "slpLatraw", "slpDurraw",
						   "slpEffraw", "slpDistraw","slpMedsraw",
						   "slpDayFcnraw", "psqi_Globalraw","ess_total",
						   "isi_total", "bdi_total", "mcgill_total",
						   "TIB")] %>%
  purrr::map(~ aov(.x ~ group.factor, data = dat1))  %>%
  # append the TukeyHSD CI estimates
  purrr::map(function(x) {
    list(
      model = x,
      tukey = TukeyHSD(x)
    )
  })

####		THIS RETURNS THE RESULTS OF THE OVERALL ANOVA	####
# GetModels <- function(l) l$model
Models3 <- purrr::map(model_summary_raw, GetModels) %>% 
  purrr::map_dfr(broom::tidy, .id = "Name")
# head(Models)

#		
Models3 <- filter(Models3,  term !="Residuals")
Models3 <- Models3 %>% 
	dplyr::select("Name" , "p.value")


####			ANOVA TABLE MADE WITH KABLE			####
Models3 %>%
	mutate(p.value = 
		   	cell_spec(
		   		(formatC(x = p.value, 
		   				 digits=3, width = 3, 
		   				 format='g', flag = "-", drop0trailing = TRUE, 
		   				 preserve.width = "common")), "html",
		   		color = ifelse(p.value <= 0.054, 
		   					   yes="red", no="blue"), escape = F)
	) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec(
			(formatC(x,digits=3, width=3, 
					 format="f", flag="-", drop0trailing = FALSE)),
			"html")}
	) %>%
	kable("html", escape = FALSE, align = "l", padding = 4,
		  caption = "ANOVA full model with raw scores") %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant main effect for group (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" )

##		END		##
```



## POSTHOC 
```{r PostHoc-Scaled, eval=TRUE, echo=TRUE, message=FALSE}
GetTukeys <- function(m) m$tukey
Tukeys  <- purrr::map(model_summaries, GetTukeys)  %>% 
	purrr::map_dfr(broom::tidy, .id = "Name")
# head(Tukeys)
# Tukeys

names(Tukeys)[names(Tukeys) == 'Name'] <- 'Var'
names(Tukeys)[names(Tukeys) == 'estimate'] <- 'diff'



####			PostHoc TABLE USING KABLE			####
select(Tukeys, -term, -Var) %>%
	mutate(adj.p.value = 
		   	cell_spec((formatC(x = adj.p.value, 
		   					   digits=3, width = 3, 
		   					   format='g', flag = "-", drop0trailing = TRUE, 
		   					   preserve.width = "common")), "html",
		   			  color = ifelse(adj.p.value <= 0.054, 
		   			  			   yes="red", no="blue"), escape = F)) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec((formatC(x,digits=3, width=3, 
						   format="f", flag="-", drop0trailing = FALSE)),
				  "html")}) %>%
	kable("html", escape = FALSE, align = "l", 
		  caption = "PostHoc group comparisons: **See** *Note* at table end",
		  padding = 2) %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant group tests (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	pack_rows(index = c(" " = 0, 
						"age_visit_1" = 3,
						"Sleep Quality" = 3,
						"Sleep Latency" = 3,
						"Sleep Duration" = 3,
						"Sleep Efficacy" = 3,
						"Sleep Disturbance" = 3,
						"Sleep Medications" = 3,
						"Sleep Daytime Functioning" = 3,
						"PSQI Global" = 3,
						"ESS Total" = 3, 
						"ISI Total" = 3,
						"BDI Total" = 3,
						"McGill Total" = 3,
						"Time in Bed" = 3)) #%>% 
# scroll_box(height = "500px")



```


```{r PostHoc-Raw, eval=FALSE, echo=TRUE, message=FALSE}
# GetTukeys <- function(m) m$tukey
Tukeys3  <- purrr::map(model_summary_raw, GetTukeys)  %>% 
	purrr::map_dfr(broom::tidy, .id = "Name")
# head(Tukeys)
# Tukeys

names(Tukeys3)[names(Tukeys3) == 'Name'] <- 'Var'
names(Tukeys3)[names(Tukeys3) == 'estimate'] <- 'diff'



####			PostHoc TABLE USING KABLE			####
select(Tukeys3, -term, -Var) %>%
	mutate(adj.p.value = 
		   	cell_spec((formatC(x = adj.p.value, 
		   					   digits=3, width = 3, 
		   					   format='g', flag = "-", drop0trailing = TRUE, 
		   					   preserve.width = "common")), "html",
		   			  color = ifelse(adj.p.value <= 0.05, 
		   			  			   yes="red", no="blue"), escape = F)) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec((formatC(x,digits=3, width=3, 
						   format="f", flag="-", drop0trailing = FALSE)),
				  "html")}) %>%
	kable("html", escape = FALSE, align = "l", 
		  caption = "PostHoc (PSQI raw) group comparisons: **See** *Note* at table end",
		  padding = 2) %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant group tests (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	pack_rows(index = c(" " = 0, 
						"age_visit_1" = 3,
						"Sleep Quality raw" = 3, 
						"Sleep Latency raw" = 3,
						"Sleep Duration raw" = 3,
						"Sleep Efficacy raw" = 3,
						"Sleep Disturbance raw" = 3,
						"Sleep Medications raw" = 3,
						"Sleep Daytime Functioning raw" = 3,
						"PSQI Global raw" = 3,
						"ESS Total" = 3, 
						"ISI Total" = 3,
						"BDI Total" = 3,
						"McGill Total" = 3,
						"Time in Bed" = 3)) #%>% 
# scroll_box(height = "500px")



```  

***   

***  

**STOP HERE  **

***  

***  

# ISI ANALYSES
This set of analyses uses a subset of subjects who have completed the ISI


Also create a dataset of subjects with ISI data (dat.isi).
```{r ISIsubgroup, eval=FALSE, echo=FALSE, message=FALSE, comment=""}
#		Subgroup with ISI data
# 		Getting selected variables
dat.isi <- dat1 %>% dplyr::select("group.factor",
										"slpQual", "slpLat", 
										"slpDur", "slpEff", 
										"slpDist", "slpMeds",
										"slpDayFcn", "psqi_Global",
										"ess_total", "isi_total",
										"bdi_total", "mcgill_total", 
										"TIB")

dat.isi2 <- dat1 %>% dplyr::select("group.factor",
										"slpQualraw", "slpLatraw", 
										"slpDurraw", "slpEffraw", 
										"slpDistraw", "slpMedsraw",
										"slpDayFcnraw", "psqi_Globalraw",
										"ess_total", "isi_total",
										"bdi_total", "mcgill_total", 
										"TIB")

#		Removing subjects without ISI data
dat.isi <- dat.isi %>% 
	na.omit()
# dim(dat.isi)

# dat.isi2 <- dat.isi2 %>% 
# 	na.omit()
# dim(dat.isi2)

# dat.isi %>% count(group.factor)
# dat.isi2 %>% count(group.factor)

```


## ISI DATA VARIANCE
The variable(s) in the ISI data with variance issues are:
```{r QA-ISI-DATA, eval=FALSE, echo=FALSE, comment=""}
nearZeroVar(dat.isi,
			uniqueCut = 2,
			names = TRUE)

```


```{r ISI-Drop-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
# dat.isi2 <- dat1 %>% dplyr::select("group.factor",
# 										"slpQualraw", "slpLatraw", 
# 										"slpDurraw", "slpEffraw", 
# 										"slpDistraw", "slpMedsraw",
# 										"slpDayFcnraw", "psqi_Globalraw",
# 										"ess_total", "isi_total",
# 										"bdi_total", "mcgill_total", 
# 										"TIB")



######		FM GROUP			####
dat.isi2 <- dat.isi2 %>% select(!"group.factor", -TIB)
# dat.isi2 <- dat.isi2 %>% select(!"group.factor")
# dat.isi2 <- dat.isi2 %>% select(!"slpDist")

####		Breaking down the plot		####

isiCorrPlot <- corr.data(dat.isi2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 3, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=2.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "ISI All groups",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
	# theme_classic() +
	# theme_cleveland() +

```


```{r ISI-ANOVA, eval=FALSE, echo=FALSE, message=FALSE}
# construct anova model for each column of dat1[, my_outcome_variables]
isi_model_summaries <- dat.isi[,c("slpQual", "slpLat", "slpDur",
						   "slpEff", "slpDist","slpMeds",
						   "slpDayFcn", "psqi_Global","ess_total",
						   "isi_total", "bdi_total", "mcgill_total",
						   "TIB")] %>%
  purrr::map(~ aov(.x ~ group.factor, data = dat.isi))  %>%
  # append the TukeyHSD CI estimates
  purrr::map(function(x) {
    list(
      model = x,
      tukey = TukeyHSD(x)
    )
  })

####		THIS RETURNS THE RESULTS OF THE OVERALL ANOVA	####
GetModels <- function(l) l$model
isi_Models <- purrr::map(isi_model_summaries, GetModels) %>% 
  purrr::map_dfr(broom::tidy, .id = "Name")
# head(Models)

#		
isi_Models2 <- filter(isi_Models,  term !="Residuals")
isi_Models2 <- isi_Models2 %>% 
	dplyr::select("Name" , "p.value")


####			ANOVA TABLE MADE WITH KABLE			####
isi_Models2 %>%
	mutate(p.value = 
		   	cell_spec(
		   		(formatC(x = p.value, 
		   				 digits=3, width = 3, 
		   				 format='g', flag = "-", drop0trailing = TRUE, 
		   				 preserve.width = "common")), "html",
		   		color = ifelse(p.value <= 0.054, 
		   					   yes="red", no="blue"), escape = F)
	) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec(
			(formatC(x,digits=3, width=3, 
					 format="f", flag="-", drop0trailing = FALSE)),
			"html")}
	) %>%
	kable("html", escape = FALSE, align = "l", padding = 4,
		  caption = "ISI subgroup ANOVA full model") %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant main effect for group (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" )

##		END		##
```


```{r ISI-PostHoc, eval=FALSE, echo=FALSE, message=FALSE}
GetTukeys <- function(m) m$tukey
isi_Tukeys  <- purrr::map(isi_model_summaries, GetTukeys)  %>% 
	purrr::map_dfr(broom::tidy, .id = "Name")
# head(Tukeys)
# Tukeys

names(isi_Tukeys)[names(isi_Tukeys) == 'Name'] <- 'Var'
names(isi_Tukeys)[names(isi_Tukeys) == 'estimate'] <- 'diff'



####			PostHoc TABLE USING KABLE			####
select(isi_Tukeys, -term, -Var) %>%
	mutate(adj.p.value = 
		   	cell_spec((formatC(x = adj.p.value, 
		   					   digits=3, width = 3, 
		   					   format='g', flag = "-", drop0trailing = TRUE, 
		   					   preserve.width = "common")), "html",
		   			  color = ifelse(adj.p.value <= 0.054, 
		   			  			   yes="red", no="blue"), escape = F)) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec((formatC(x,digits=3, width=3, 
						   format="f", flag="-", drop0trailing = FALSE)),
				  "html")}) %>%
	kable("html", escape = FALSE, align = "l", 
		  caption = "PostHoc group comparisons: **See** *Note* at table end",
		  padding = 2) %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant group tests (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	pack_rows(index = c(" " = 0, "Sleep Quality" = 3, #)) #, 
						"Sleep Latency" = 3,
						"Sleep Duration" = 3,
						"Sleep Efficacy" = 3,
						"Sleep Disturbance" = 3,
						"Sleep Medications" = 3,
						"Sleep Daytime Functioning" = 3,
						"PSQI Global" = 3,
						"ESS Total" = 3, 
						"ISI Total" = 3,
						"BDI Total" = 3,
						"McGill Total" = 3,
						"Time in Bed" = 3)) #%>% 
# scroll_box(height = "500px")



```



# END - BEYOND HERE IS EXPLORATORY
