---
title: "Untitled"
author: "Jason"
date: "12/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#				MOOD t-test
```{r Mood_Subset, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}

#	Need to compare mood pre positive by group
#	Need to compare mood pre negative by group
#	Need to compare mood post positive by group
#	Need to compare mood post negative by group

##			USED FOR FINDING ORIGINAL VARIABLES		##
colnames(select(dat1, contains("mood")))
colnames(select(dat1, contains("cond")))

dat1 %>% count(group.factor)

# v1Pos1_dat <- dat1 %>%
# 	filter(dat1$v1mood.factor == "PosV1")
# v1Pos1_dat %>% count(group.factor)
# v1Pos1_dat2 %>% count(gp)

v1Pos1.dat <- dat1 %>% dplyr::select("ID","group.factor",
									 "v1mood.factor",
									 "visit1moodpre") %>% 
	filter(group.factor != "NA")

v1Pos1.dat2 <- v1Pos1_dat %>% 
	filter(v1mood.factor == "PosV1") %>% 
	filter(visit1moodpre != "NA")



view(v1Pos1.dat)
view(v1Pos1.dat2)

names(v1Pos1.dat)[names(v1Pos1.dat) == 'group.factor'] <- 'gp'
names(v1Pos1.dat)[names(v1Pos1.dat) == 'v1mood.factor'] <- 'v1mood'

#		Converting data to long format
dat2 <- dat1 %>% dplyr::select("ID", "group.factor",
								"v1.mood", "v2.mood",
								"visit1moodpre", "visit1moodpost",
								# contains("mood")
								"visit2moodpre", "visit2moodpost"
								)

# dat1  <- filter(dat1, group.factor != 0, dat1$bdi1 != "NA")
dat2 <- filter(dat2, dat2$visit1moodpre != "NA")

dat2$ID <- factor(dat2$ID) # ID must be a factor

dat2 %>% count(group.factor)






v1Neg1.dat <- dat1 %>%
	filter(v1mood.factor == "NegV1")
v1Neg1.dat %>% count(group.factor)


v1Pos2.dat <- dat1 %>%
	filter(v2mood.factor == "PosV2")
v1Pos2.dat %>% count(group.factor)

v1Neg2.dat <- dat1 %>%
	filter(v2mood.factor == "NegV2")
v1Neg2.dat %>% count(group.factor)



#	t-tests are needed for:
#		1.	(data = dat1) visit1moodpre vs group.factor

#	1. T-test
# dat2 %>% filter(group.factor != "FM") %>% 
# t.test(dat2$visit1moodpre ~ dat2$group.factor, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
# #		Result (NS) = no significant differences between groups for mood pre manipulation

#	T-tests are needed for (Positive mood)	####
#		1.	(data = v1Pos1) visit1moodpre vs. visit1moodpost
#		2.	(data = v1Pos1) visit1moodpre by group.factor
#		3.	(data = v1Pos1) visit1moodpost by group.factor
#		4.	(data = v1Pos1) visit1moodchange by group.factor
#		5.	(data = v1Pos1, filter = HC) visit1moodpre vs. visit1moodpost
#		6.	(data = v1Pos1, filter = FM) visit1moodpre vs. visit1moodpost

#	1. T-test
t.test(v1Pos1.dat$visit1moodpre, v1Pos1.dat$visit1moodpost,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (sig): Across groups mood significantly improved from pre to post
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpre and v1Pos1.dat$visit1moodpost
# t = -3.868, df = 81.755, p-value = 0.0002194
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -3.175129 -1.018330
# sample estimates:
# mean of x mean of y 
#  3.488636  5.585366 


v1pos2gp <- v1pos_dat %>% filter(group.factor != "FM")
v2pos2gp <- v2pos_dat %>% filter(group.factor != "FM")

v1neg2gp <- v1neg_dat %>% filter(group.factor != "FM")
v2neg2gp <- v2neg_dat %>% filter(group.factor != "FM")

#	2. T-test		#####
t.test(v1pos2gp$pos_pre ~ v1pos2gp$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

t.test(v2pos2gp$pos_pre ~ v2pos2gp$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

t.test(v1neg2gp$neg_pre ~ v1neg2gp$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

t.test(v2neg2gp$neg_pre ~ v2neg2gp$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)


#		RESULT (NS): There is a trend toward significance but both HC = CLBP pre positive mood
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpre by v1Pos1.dat$group.factor
# t = 1.9084, df = 22.469, p-value = 0.0692
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -0.1272539  3.1074028
# sample estimates:
#   mean in group HC mean in group CLBP 
#           4.538462           3.048387 

#	3. T-test	####
t.test(v1Pos1.dat$visit1moodpost ~ v1Pos1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT(sig): There is a significant group difference in post positive mood (HC > CLBP) 
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpost by v1Pos1.dat$group.factor
# t = 2.3443, df = 30.961, p-value = 0.02566
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  0.225306 3.241727
# sample estimates:
#   mean in group HC mean in group CLBP 
#           6.769231           5.035714 



#	4. T-test	####
t.test(v1Pos1.dat$v1moodchange ~ v1Pos1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There doesn’t seem to be a significant difference in mood change 
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$v1moodchange by v1Pos1.dat$group.factor
# t = 0.056369, df = 18.251, p-value = 0.9557
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -1.244313  1.312994
# sample estimates:
#   mean in group HC mean in group CLBP 
#           2.230769           2.196429 



#	T-tests are needed for (Negative mood)
#		1.	(data = v1Neg1) visit1moodpre vs. visit1moodpost
#		2.	(data = v1Neg1) visit1moodpre by group.factor
#		3.	(data = v1Neg1) visit1moodpost by group.factor
#		4.	(data = v1Neg1) visit1moodchange by group.factor
#		5.	(data = v1Neg1, filter = HC) visit1moodpre vs. visit1moodpost
#		6.	(data = v1Neg1, filter = FM) visit1moodpre vs. visit1moodpost


#	1. T-test
t.test(v1Neg1.dat$visit1moodpre, v1Neg1.dat$visit1moodpost,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (SIG): Across groups there is a change in negative mood (pre < post)
#
# 	Welch Two Sample t-test
# data:  v1Neg1.dat$visit1moodpre and v1Neg1.dat$visit1moodpost
# t = -8.5595, df = 89.102, p-value = 3.038e-13
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -4.357135 -2.715365
# sample estimates:
# mean of x mean of y 
#   1.12000   4.65625 


#	2. T-test
t.test(v1Neg1.dat$visit1moodpre ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There is no group difference in pre negative mood

# 	Welch Two Sample t-test
# 
# data:  v1Neg1.dat$visit1moodpre by v1Neg1.dat$group.factor
# t = -1.1198, df = 45.142, p-value = 0.2687
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -1.4964441  0.4269997
# sample estimates:
#   mean in group HC mean in group CLBP 
#          0.7777778          1.3125000 



#	3. T-test
t.test(v1Neg1.dat$visit1moodpost ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT(NS): There is no group difference in post negative mood

# 	Welch Two Sample t-test
# data:  v1Neg1.dat$visit1moodpost by v1Neg1.dat$group.factor
# t = -1.5044, df = 41.11, p-value = 0.1401
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -2.2511924  0.3289702
# sample estimates:
#   mean in group HC mean in group CLBP 
#           4.055556           5.016667 



#	4. T-test
t.test(v1Neg1.dat$v1moodchange ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There does not seem to be a significant difference in mood change 
#
# 	Welch Two Sample t-test
# data:  v1Neg1.dat$v1moodchange by v1Neg1.dat$group.factor
# t = -0.84463, df = 45.761, p-value = 0.4027
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -2.0489069  0.8377958
# sample estimates:
#   mean in group HC mean in group CLBP 
#           3.277778           3.883333 













dat1.mood <- dat1

dat1.mood  <- dat1.mood %>% dplyr::select("ID","group.factor",
										  )


levels(dat1$v1mood.factor)

```

```{r test, eval=TRUE, echo=FALSE, message=FALSE, comment = ""}
#		5. t-test neg_pre vs neg_post	####
#	1. T-test
t.test(twoGpMood$neg_pre, twoGpMood$neg_post,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)


#		6. t-test neg_pre by group		####
#	2. T-test (data = twoGpMood)
t.test(twoGpMood$neg_pre ~ twoGpMood$group,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)


#		7. t-test neg_post by group	####
#	3. T-test (data = twoGpMood)
t.test(twoGpMood$neg_post ~ twoGpMood$group,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

#		8. t-test neg_chng by group	####
#	4. T-test 	(data = twoGpMood)
t.test(twoGpMood$neg_chng ~ twoGpMood$group,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)




```






#				OLD T-TESTS
##				MOOD t-test
```{r Mood_Subset, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}

#	Need to compare mood pre positive by group
#	Need to compare mood pre negative by group
#	Need to compare mood post positive by group
#	Need to compare mood post negative by group

##			USED FOR FINDING ORIGINAL VARIABLES		##
colnames(select(dat1, contains("mood")))
colnames(select(dat1, contains("cond")))

dat1 %>% count(group.factor)

# v1Pos1_dat <- dat1 %>%
# 	filter(dat1$v1mood.factor == "PosV1")
# v1Pos1_dat %>% count(group.factor)
# v1Pos1_dat2 %>% count(gp)

v1Pos1.dat <- dat1 %>% dplyr::select("ID","group.factor",
									 "v1mood.factor",
									 "visit1moodpre") %>% 
	filter(group.factor != "NA")

v1Pos1.dat2 <- v1Pos1_dat %>% 
	filter(v1mood.factor == "PosV1") %>% 
	filter(visit1moodpre != "NA")



view(v1Pos1.dat)
view(v1Pos1.dat2)

names(v1Pos1.dat)[names(v1Pos1.dat) == 'group.factor'] <- 'gp'
names(v1Pos1.dat)[names(v1Pos1.dat) == 'v1mood.factor'] <- 'v1mood'

#		Converting data to long format
dat2 <- dat1 %>% dplyr::select("ID", "group.factor",
								"v1.mood", "v2.mood",
								"visit1moodpre", "visit1moodpost",
								# contains("mood")
								"visit2moodpre", "visit2moodpost"
								)

# dat1  <- filter(dat1, group.factor != 0, dat1$bdi1 != "NA")
dat2 <- filter(dat2, dat2$visit1moodpre != "NA")

dat2$ID <- factor(dat2$ID) # ID must be a factor

dat2 %>% count(group.factor)






v1Neg1.dat <- dat1 %>%
	filter(v1mood.factor == "NegV1")
v1Neg1.dat %>% count(group.factor)


v1Pos2.dat <- dat1 %>%
	filter(v2mood.factor == "PosV2")
v1Pos2.dat %>% count(group.factor)

v1Neg2.dat <- dat1 %>%
	filter(v2mood.factor == "NegV2")
v1Neg2.dat %>% count(group.factor)



#	t-tests are needed for:
#		1.	(data = dat1) visit1moodpre vs group.factor

#	1. T-test
# dat2 %>% filter(group.factor != "FM") %>% 
# t.test(dat2$visit1moodpre ~ dat2$group.factor, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
# #		Result (NS) = no significant differences between groups for mood pre manipulation

#	T-tests are needed for (Positive mood)
#		1.	(data = v1Pos1) visit1moodpre vs. visit1moodpost
#		2.	(data = v1Pos1) visit1moodpre by group.factor
#		3.	(data = v1Pos1) visit1moodpost by group.factor
#		4.	(data = v1Pos1) visit1moodchange by group.factor
#		5.	(data = v1Pos1, filter = HC) visit1moodpre vs. visit1moodpost
#		6.	(data = v1Pos1, filter = FM) visit1moodpre vs. visit1moodpost

#	1. T-test
t.test(v1Pos1.dat$visit1moodpre, v1Pos1.dat$visit1moodpost,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (sig): Across groups mood significantly improved from pre to post
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpre and v1Pos1.dat$visit1moodpost
# t = -3.868, df = 81.755, p-value = 0.0002194
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -3.175129 -1.018330
# sample estimates:
# mean of x mean of y 
#  3.488636  5.585366 



#	2. T-test
t.test(v1Pos1.dat$visit1moodpre ~ v1Pos1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There is a trend toward significance but both HC = CLBP pre positive mood
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpre by v1Pos1.dat$group.factor
# t = 1.9084, df = 22.469, p-value = 0.0692
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -0.1272539  3.1074028
# sample estimates:
#   mean in group HC mean in group CLBP 
#           4.538462           3.048387 

#	3. T-test
t.test(v1Pos1.dat$visit1moodpost ~ v1Pos1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT(sig): There is a significant group difference in post positive mood (HC > CLBP) 
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$visit1moodpost by v1Pos1.dat$group.factor
# t = 2.3443, df = 30.961, p-value = 0.02566
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  0.225306 3.241727
# sample estimates:
#   mean in group HC mean in group CLBP 
#           6.769231           5.035714 



#	4. T-test
t.test(v1Pos1.dat$v1moodchange ~ v1Pos1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There doesn’t seem to be a significant difference in mood change 
#
# 	Welch Two Sample t-test
# data:  v1Pos1.dat$v1moodchange by v1Pos1.dat$group.factor
# t = 0.056369, df = 18.251, p-value = 0.9557
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -1.244313  1.312994
# sample estimates:
#   mean in group HC mean in group CLBP 
#           2.230769           2.196429 



#	T-tests are needed for (Positive mood)
#		1.	(data = v1Neg1) visit1moodpre vs. visit1moodpost
#		2.	(data = v1Neg1) visit1moodpre by group.factor
#		3.	(data = v1Neg1) visit1moodpost by group.factor
#		4.	(data = v1Neg1) visit1moodchange by group.factor
#		5.	(data = v1Neg1, filter = HC) visit1moodpre vs. visit1moodpost
#		6.	(data = v1Neg1, filter = FM) visit1moodpre vs. visit1moodpost


#	1. T-test
t.test(v1Neg1.dat$visit1moodpre, v1Neg1.dat$visit1moodpost,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (SIG): Across groups there is a change in negative mood (pre < post)
#
# 	Welch Two Sample t-test
# data:  v1Neg1.dat$visit1moodpre and v1Neg1.dat$visit1moodpost
# t = -8.5595, df = 89.102, p-value = 3.038e-13
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -4.357135 -2.715365
# sample estimates:
# mean of x mean of y 
#   1.12000   4.65625 


#	2. T-test
t.test(v1Neg1.dat$visit1moodpre ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There is no group difference in pre negative mood

# 	Welch Two Sample t-test
# 
# data:  v1Neg1.dat$visit1moodpre by v1Neg1.dat$group.factor
# t = -1.1198, df = 45.142, p-value = 0.2687
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -1.4964441  0.4269997
# sample estimates:
#   mean in group HC mean in group CLBP 
#          0.7777778          1.3125000 



#	3. T-test
t.test(v1Neg1.dat$visit1moodpost ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT(NS): There is no group difference in post negative mood

# 	Welch Two Sample t-test
# data:  v1Neg1.dat$visit1moodpost by v1Neg1.dat$group.factor
# t = -1.5044, df = 41.11, p-value = 0.1401
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -2.2511924  0.3289702
# sample estimates:
#   mean in group HC mean in group CLBP 
#           4.055556           5.016667 



#	4. T-test
t.test(v1Neg1.dat$v1moodchange ~ v1Neg1.dat$group.factor,
	   mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
#		RESULT (NS): There does not seem to be a significant difference in mood change 
#
# 	Welch Two Sample t-test
# data:  v1Neg1.dat$v1moodchange by v1Neg1.dat$group.factor
# t = -0.84463, df = 45.761, p-value = 0.4027
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -2.0489069  0.8377958
# sample estimates:
#   mean in group HC mean in group CLBP 
#           3.277778           3.883333 













dat1.mood <- dat1

dat1.mood  <- dat1.mood %>% dplyr::select("ID","group.factor",
										  )


levels(dat1$v1mood.factor)

```



## Group by age for overall sample.
```{r Gp_by_age, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}
newdf <- df %>% filter(party %in% c('R','D')) %>%
  group_by(termstart,party) %>% summarise(MeanAge=mean(age,na.rm=T)) %>%
  pivot_wider(names_from = party,values_from=MeanAge)

newdf <- dat1 %>% filter(group.factor %in% c('HC','CLBP', 'FM')) %>%
	group_by(group.factor) %>%
	summarise(MeanAge=mean(age_visit_1,na.rm=T), 
			  ageSD=sd(age_visit_1, na.rm = T)) 


#%>%
	pivot_longer(newdf,
				 group.factor,
				 names_from = group.factor,values_from=MeanAge)
#	pivot_wider(names_from = group.factor,values_from=MeanAge)
	
```


# TABLES
```{r table, eval=TRUE, echo=FALSE, message=FALSE, comment = ""}

gpsex1 %>% 
	kable(align = "c", padding = 4, caption = "Entire Sample") %>% 
	kable_styling(c("striped", "bordered"), full_width = F) %>% 
	add_header_above(c(" ", "Sex" = 2, "")) %>%
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	row_spec(4, bold = T, background = "lightgrey") %>% 
	column_spec(4, bold = T, background = "lightgray")

```

### t-test Age 2 groups
```{r ttest_Age, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}

##		FINAL SUBJECT COUNT		##
# dat1 %>% count(group.factor)
# dat2  <-  filter(dat1, group.factor != "FM")

# age.dat   <- dat1
# # age.dat   <- filter(dat1, group.factor != "FM")
# # age.dat2 <- droplevels(age.dat)
# age.dat %>% count(group.factor)
# age.dat2 %>% count(group.factor)
dat2 %>% count(group.factor)

##		FINAL SUBJECT COUNT		##
# dat2  <-  filter(dat1, group.factor != "FM")

# attach(age.dat)
boxplot(dat1$age_visit_1 ~ dat1$group)
# boxplot(age.dat2$age_visit_1 ~ age.dat2$group)

# dat3 <- dat2 %>% filter(group.factor != "FM") 

# dat4 <- droplevels(dat3)
# 
# str(age.dat)
# 			  
# boxplot()
			# table(droplevels(aq)$Month)


# %>% 
# boxplot(visit1moodpre ~ group.factor,data = dat1)

# Ho: mean age of HC = CLBP
# two-sided test
# assume non-equal variances

ageGroup.dat <- t.test(dat1$age_visit_1 ~ dat1$group.factor, mu=0, 
					   alt="two.sided", conf=0.95, var.eq=F, paired=F)
ageGroup.dat

# 	Welch Two Sample t-test
# 
# data:  dat1$age_visit_1 by dat1$group.factor
# t = -4.6149, df = 67.795, p-value = 1.802e-05
# alternative hypothesis: true difference in means is not equal to 0
# 95 percent confidence interval:
#  -11.914839  -4.721086
# sample estimates:
#   mean in group HC mean in group CLBP 
#           24.79230           33.11026 








v1MoodPre.ttest <- t.test(age.dat$visit1moodpre ~ age.dat$group.factor, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
v1MoodPre.ttest


t.test(age.dat$visit1moodpre ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)
t.test(age.dat$visit1moodpost ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)


t.test(age.dat$visit1moodpost ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)


# ageEd.dat <- t.test(age.dat$education ~ age.dat$group, mu=0, alt="two.sided", conf=0.95, var.eq=F, paired=F)

ageGroup.dat

	
```






##		ANOVA Raw
```{r ANOVA-rawdata, eval=FALSE, echo=TRUE, message=FALSE}
#		USING PSQI RAW COMPONENT SCORES
# construct anova model for each column of dat1[, my_outcome_variables]
model_summary_raw <- dat1[,c("age_visit_1", "slpQualraw", "slpLatraw", "slpDurraw",
						   "slpEffraw", "slpDistraw","slpMedsraw",
						   "slpDayFcnraw", "psqi_Globalraw","ess_total",
						   "isi_total", "bdi_total", "mcgill_total",
						   "TIB")] %>%
  purrr::map(~ aov(.x ~ group.factor, data = dat1))  %>%
  # append the TukeyHSD CI estimates
  purrr::map(function(x) {
    list(
      model = x,
      tukey = TukeyHSD(x)
    )
  })

####		THIS RETURNS THE RESULTS OF THE OVERALL ANOVA	####
# GetModels <- function(l) l$model
Models3 <- purrr::map(model_summary_raw, GetModels) %>% 
  purrr::map_dfr(broom::tidy, .id = "Name")
# head(Models)

#		
Models3 <- filter(Models3,  term !="Residuals")
Models3 <- Models3 %>% 
	dplyr::select("Name" , "p.value")


####			ANOVA TABLE MADE WITH KABLE			####
Models3 %>%
	mutate(p.value = 
		   	cell_spec(
		   		(formatC(x = p.value, 
		   				 digits=3, width = 3, 
		   				 format='g', flag = "-", drop0trailing = TRUE, 
		   				 preserve.width = "common")), "html",
		   		color = ifelse(p.value <= 0.054, 
		   					   yes="red", no="blue"), escape = F)
	) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec(
			(formatC(x,digits=3, width=3, 
					 format="f", flag="-", drop0trailing = FALSE)),
			"html")}
	) %>%
	kable("html", escape = FALSE, align = "l", padding = 4,
		  caption = "ANOVA full model with raw scores") %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant main effect for group (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" )

##		END		##
```



##		Post Hoc Raw
```{r PostHoc-Raw, eval=FALSE, echo=TRUE, message=FALSE}
# GetTukeys <- function(m) m$tukey
Tukeys3  <- purrr::map(model_summary_raw, GetTukeys)  %>% 
	purrr::map_dfr(broom::tidy, .id = "Name")
# head(Tukeys)
# Tukeys

names(Tukeys3)[names(Tukeys3) == 'Name'] <- 'Var'
names(Tukeys3)[names(Tukeys3) == 'estimate'] <- 'diff'



####			PostHoc TABLE USING KABLE			####
select(Tukeys3, -term, -Var) %>%
	mutate(adj.p.value = 
		   	cell_spec((formatC(x = adj.p.value, 
		   					   digits=3, width = 3, 
		   					   format='g', flag = "-", drop0trailing = TRUE, 
		   					   preserve.width = "common")), "html",
		   			  color = ifelse(adj.p.value <= 0.05, 
		   			  			   yes="red", no="blue"), escape = F)) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec((formatC(x,digits=3, width=3, 
						   format="f", flag="-", drop0trailing = FALSE)),
				  "html")}) %>%
	kable("html", escape = FALSE, align = "l", 
		  caption = "PostHoc (PSQI raw) group comparisons: **See** *Note* at table end",
		  padding = 2) %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant group tests (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	pack_rows(index = c(" " = 0, 
						"age_visit_1" = 3,
						"Sleep Quality raw" = 3, 
						"Sleep Latency raw" = 3,
						"Sleep Duration raw" = 3,
						"Sleep Efficacy raw" = 3,
						"Sleep Disturbance raw" = 3,
						"Sleep Medications raw" = 3,
						"Sleep Daytime Functioning raw" = 3,
						"PSQI Global raw" = 3,
						"ESS Total" = 3, 
						"ISI Total" = 3,
						"BDI Total" = 3,
						"McGill Total" = 3,
						"Time in Bed" = 3)) #%>% 
# scroll_box(height = "500px")



```  

***   

***  

**STOP HERE  **

***  

***  

# ISI ANALYSES
This set of analyses uses a subset of subjects who have completed the ISI


Also create a dataset of subjects with ISI data (dat.isi).
```{r ISIsubgroup, eval=FALSE, echo=FALSE, message=FALSE, comment=""}
#		Subgroup with ISI data
# 		Getting selected variables
dat.isi <- dat1 %>% dplyr::select("group.factor",
										"slpQual", "slpLat", 
										"slpDur", "slpEff", 
										"slpDist", "slpMeds",
										"slpDayFcn", "psqi_Global",
										"ess_total", "isi_total",
										"bdi_total", "mcgill_total", 
										"TIB")

dat.isi2 <- dat1 %>% dplyr::select("group.factor",
										"slpQualraw", "slpLatraw", 
										"slpDurraw", "slpEffraw", 
										"slpDistraw", "slpMedsraw",
										"slpDayFcnraw", "psqi_Globalraw",
										"ess_total", "isi_total",
										"bdi_total", "mcgill_total", 
										"TIB")

#		Removing subjects without ISI data
dat.isi <- dat.isi %>% 
	na.omit()
dim(dat.isi)

# dat.isi2 <- dat.isi2 %>% 
# 	na.omit()
# dim(dat.isi2)

# dat.isi %>% count(group.factor)
# dat.isi2 %>% count(group.factor)

```


## ISI DATA VARIANCE
The variable(s) in the ISI data with variance issues are:
```{r QA-ISI-DATA, eval=FALSE, echo=FALSE, comment=""}
nearZeroVar(dat.isi,
			uniqueCut = 2,
			names = TRUE)

```


```{r ISI-Drop-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
# dat.isi2 <- dat1 %>% dplyr::select("group.factor",
# 										"slpQualraw", "slpLatraw", 
# 										"slpDurraw", "slpEffraw", 
# 										"slpDistraw", "slpMedsraw",
# 										"slpDayFcnraw", "psqi_Globalraw",
# 										"ess_total", "isi_total",
# 										"bdi_total", "mcgill_total", 
# 										"TIB")



######		FM GROUP			####
dat.isi2 <- dat.isi2 %>% select(!"group.factor", -TIB)
# dat.isi2 <- dat.isi2 %>% select(!"group.factor")
# dat.isi2 <- dat.isi2 %>% select(!"slpDist")

####		Breaking down the plot		####

isiCorrPlot <- corr.data(dat.isi2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 3, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=2.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "ISI All groups",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
	# theme_classic() +
	# theme_cleveland() +

```


```{r ISI-ANOVA, eval=FALSE, echo=FALSE, message=FALSE}
dat.isi <- as_tibble(dat.isi)

# construct anova model for each column of dat1[, my_outcome_variables]
isi_model_summaries <- dat.isi[,c("group.factor","slpQual", "slpLat", "slpDur",
						   "slpEff", "slpDist","slpMeds",
						   "slpDayFcn", "psqi_Global","ess_total",
						   "isi_total", "bdi_total", "mcgill_total",
						   "TIB")] %>%
  purrr::map(~ aov(.x ~ group.factor, data = dat.isi))  %>%
  # append the TukeyHSD CI estimates
  purrr::map(function(x) {
    list(
      model = x,
      tukey = TukeyHSD(x)
    )
  })


head(dat.isi)



####		THIS RETURNS THE RESULTS OF THE OVERALL ANOVA	####
GetModels <- function(l) l$model
isi_Models <- purrr::map(isi_model_summaries, GetModels) %>% 
  purrr::map_dfr(broom::tidy, .id = "Name")
# head(Models)

#		
isi_Models2 <- filter(isi_Models,  term !="Residuals")
isi_Models2 <- isi_Models2 %>% 
	dplyr::select("Name" , "p.value")


####			ANOVA TABLE MADE WITH KABLE			####
isi_Models2 %>%
	mutate(p.value = 
		   	cell_spec(
		   		(formatC(x = p.value, 
		   				 digits=3, width = 3, 
		   				 format='g', flag = "-", drop0trailing = TRUE, 
		   				 preserve.width = "common")), "html",
		   		color = ifelse(p.value <= 0.054, 
		   					   yes="red", no="blue"), escape = F)
	) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec(
			(formatC(x,digits=3, width=3, 
					 format="f", flag="-", drop0trailing = FALSE)),
			"html")}
	) %>%
	kable("html", escape = FALSE, align = "l", padding = 4,
		  caption = "ISI subgroup ANOVA full model") %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant main effect for group (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" )

##		END		##
```


```{r ISI-PostHoc, eval=FALSE, echo=FALSE, message=FALSE}
GetTukeys <- function(m) m$tukey
isi_Tukeys  <- purrr::map(isi_model_summaries, GetTukeys)  %>% 
	purrr::map_dfr(broom::tidy, .id = "Name")
# head(Tukeys)
# Tukeys

names(isi_Tukeys)[names(isi_Tukeys) == 'Name'] <- 'Var'
names(isi_Tukeys)[names(isi_Tukeys) == 'estimate'] <- 'diff'



####			PostHoc TABLE USING KABLE			####
select(isi_Tukeys, -term, -Var) %>%
	mutate(adj.p.value = 
		   	cell_spec((formatC(x = adj.p.value, 
		   					   digits=3, width = 3, 
		   					   format='g', flag = "-", drop0trailing = TRUE, 
		   					   preserve.width = "common")), "html",
		   			  color = ifelse(adj.p.value <= 0.054, 
		   			  			   yes="red", no="blue"), escape = F)) %>% 
	mutate_if(is.numeric, function(x) {
		cell_spec((formatC(x,digits=3, width=3, 
						   format="f", flag="-", drop0trailing = FALSE)),
				  "html")}) %>%
	kable("html", escape = FALSE, align = "l", 
		  caption = "PostHoc group comparisons: **See** *Note* at table end",
		  padding = 2) %>%
	kable_styling(c("striped", "bordered", "hover"), full_width = F) %>%
	footnote(general = "Red = Significant group tests (p ≤ 0.05)")  %>% 
	row_spec(0, bold = T, color = "white", background = "#461B7E" ) %>% 
	pack_rows(index = c(" " = 0, "Sleep Quality" = 3, #)) #, 
						"Sleep Latency" = 3,
						"Sleep Duration" = 3,
						"Sleep Efficacy" = 3,
						"Sleep Disturbance" = 3,
						"Sleep Medications" = 3,
						"Sleep Daytime Functioning" = 3,
						"PSQI Global" = 3,
						"ESS Total" = 3, 
						"ISI Total" = 3,
						"BDI Total" = 3,
						"McGill Total" = 3,
						"Time in Bed" = 3)) #%>% 
# scroll_box(height = "500px")



```



# END - BEYOND HERE IS EXPLORATORY




## BAR PLOTS
```{r BARS-1, eval=FALSE, echo=FALSE, message=FALSE}
dat.bar1.orig  <- dat1 %>% dplyr::select("ID","group.factor",
										 "slpQual", "slpLat", 
										 "slpDur", "slpEff", 
										 "slpDayFcn", "psqi_Global",
										 "ess_total", "bdi_total", 
										 "mcgill_total")

dat.bar1.orig$ID <- factor(dat.bar1.orig$ID) # ID must be a factor
names(dat.bar1.orig)[names(dat.bar1.orig)=="group.factor"] <- "group"


####			BAR CHART DATA NEED TO BE IN LONG FORMAT		####

#		Plot all the data at once
dat.bar0 <- dat.bar1.orig

#	select data for 1st bar chart = BDI, ESS, McGill
dat.bar1a <- select(dat.bar1.orig, ID, group, 
					slpDayFcn, slpEff, slpDur,
					slpQual, slpLat)

#	select data for 2nd bar chart
dat.bar1b <- select(dat.bar1.orig, ID, group, 
				   ess_total, psqi_Global, bdi_total)

#	select data for 3rd bar chart
dat.bar1c <- select(dat.bar1.orig, ID, group, 
					mcgill_total)

#	select data for 3rd bar chart
dat.bar1d <- select(dat.bar1.orig, ID, group, 
					mcgill_total, psqi_Global)




# str(dat.bar)

#		Convert to long format
bar0.melt <- melt(dat.bar0, id.vars = c("ID", "group")) 
bar1a.melt <- melt(dat.bar1a, id.vars = c("ID", "group")) 
bar1b.melt <- melt(dat.bar1b, id.vars = c("ID", "group"))
bar1c.melt <- melt(dat.bar1c, id.vars = c("ID", "group"))
bar1d.melt <- melt(dat.bar1d, id.vars = c("ID", "group"))

# head(bar1a.melt)

#		Rename "value"
names(bar0.melt)[names(bar0.melt)=="value"] <- "score"
names(bar1a.melt)[names(bar1a.melt)=="value"] <- "score"
names(bar1b.melt)[names(bar1b.melt)=="value"] <- "score"
names(bar1c.melt)[names(bar1c.melt)=="value"] <- "score"
names(bar1d.melt)[names(bar1d.melt)=="value"] <- "score"


#		Calculate means and sem
bar0.means <- ddply(bar0.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sd = sd(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1a.means <- ddply(bar1a.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)


bar1b.means <- ddply(bar1b.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1c.means <- ddply(bar1c.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)

bar1d.means <- ddply(bar1d.melt, c("group", "variable"),
					summarise,
					mean = mean(score),
					sem = sd(score)/sqrt(length(score)),
					lsem = mean - sem,
					usem = mean + sem)


#		PLOT THE LONG DATA
ggplot(bar0.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,40)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	# scale_x_discrete(limits = vlevels1a) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons of all vars") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) 


ggplot(bar1a.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,2.5)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons of psqi vars") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) 


ggplot(bar1b.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	# coord_cartesian(ylim = c(0,3)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "Group comparisons")

ggplot(bar1c.means, aes(x = variable, y = mean, fill = group )) +
	geom_bar(position = position_dodge(.9), colour = "black", 
			 stat = "identity") +
	geom_errorbar(position = position_dodge(.9), width = .25,
				  aes(ymin = mean - sem, ymax = mean + sem)) +
	coord_cartesian(ylim = c(0,40)) +
	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
	scale_y_continuous(breaks = waiver()) +
	geom_hline(yintercept = 0) +
	labs(title = "McGill pain questionnaire")

# ggplot(bar1d.means, aes(x = variable, y = mean, fill = group )) +
# 	geom_bar(position = position_dodge(.9), colour = "black", 
# 			 stat = "identity") +
# 	geom_errorbar(position = position_dodge(.9), width = .25,
# 				  aes(ymin = mean - sem, ymax = mean + sem)) +
# 	# coord_cartesian(ylim = c(0,40)) +
# 	scale_fill_manual(values = c("#19c01a", "#1349ec", "#ec1313")) +
# 	scale_y_continuous(breaks = waiver()) +
# 	geom_hline(yintercept = 0)


```


```{r BARPLOT-test, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}

#		VISUALIZE THE GROUP DIFFERENCES	WITH SIG LEVELS		#
# Bar plot of mean +/-se
ggbarplot(ToothGrowth, x = "dose", y = "len", add = "mean_se")+
  stat_compare_means() +                                         # Global p-value
  stat_compare_means(ref.group = "0.5", label = "p.signif",
                     label.y = c(22, 29))                   # compare to ref.group

# Line plot of mean +/-se
ggline(ToothGrowth, x = "dose", y = "len", add = "mean_se")+
  stat_compare_means() +                                         # Global p-value
  stat_compare_means(ref.group = "0.5", label = "p.signif",
                     label.y = c(22, 29))     

# _________________________________________#
#		EXAMPLE		#

zdat <- data.frame(Group = c("S1", "S1", "S2", "S2"),
              Sub   = c("A", "B", "A", "B"),
              Value = c(3,5,7,8))  

ggplot(zdat, aes(Group, Value)) +
	geom_bar(aes(fill = Sub), stat="identity", 
			 position="dodge", width=.5) +
	geom_signif(stat="identity",
				data=data.frame(x=c(0.875, 1.875),
								xend=c(1.125, 2.125),
								y=c(5.8, 8.5), 
								annotation=c("**", "NS")),
				aes(x=x,xend=xend, y=y, yend=y,
					annotation=annotation)) #+
	geom_signif(comparisons=list(c("S1", "S2")),
				annotations="***",
				y_position = 9.3, 
				tip_length = 0, vjust=0.4) 
# +
	# scale_fill_manual(values = c("grey80", "grey20"))

#___________________________________________#
library(ggplot2)
library(ggpval)
data("PlantGrowth")
plt <- ggplot(PlantGrowth, aes(group, weight)) +
  geom_boxplot()
add_pval(plt, pairs = list(c(1, 3)), test='wilcox.test')
#_________________________________________

ggplot(bar1a.means, aes(variable, mean)) +
	geom_bar(aes(fill = group),
			 stat = "identity",
			 position = "dodge", 
			 width = .5) +
	geom_signif(stat = "identity",
				data=data.frame(x=c(0.875, 1.875),
								xend=c(1.125, 2.125),
								y=c(2.5, 3.5), 
								annotation=c("***", "bob")),
				aes(x=x,xend=xend, y=y, yend=y,
					annotation=annotation))

```


#		Plots
## BOX PLOTS
```{r Box-plots, eval=FALSE, echo=FALSE, message=FALSE}
####		PSQI BOXPLOT		####
head(dat.bar1a)
head(bar1a.means)
ggplot(bar1a.means, aes(x = group, y = mean )) +
	geom_boxplot() +
	geom_signif(comparisons = list(c("HC", "CLBP"),
								   c("HC", "FM"),
								   c("CLBP", "FM")),
				 # y_position = c(30, 40, 25),
				map_signif_level=function(p)sprintf("p = %.2g", p))



```


```{r BOXPLOT-test, eval=FALSE, echo=FALSE, message=FALSE, comment = ""}
# PERFORMING TEST
compare_means(mcgill_total ~ group.factor, data = dat1,
			  ref.group = ".all.", method = "t.test")


#		VISUALIZE THE GROUP DIFFERENCES			#
# 		Pairwise comparison of all agains the grand mean (I think)
ggboxplot(dat1, x = "group.factor",
		  y = "mcgill_total",
		  color = "group.factor",
		  add = "jitter",
		  legend = "none") +
	rotate_x_text(angle = 45) +
	geom_hline(yintercept = mean(dat1$mcgill_total),
			   linetype = 2) + # add horizontal line at base mean
	stat_compare_means(method = "anova", label.y = 80) +
	stat_compare_means(label = "p.signif",
					   method = "t.test",
					   ref.group = ".all.")  

#		VISUALIZE GROUP DIFS WITH SIG LEVELS IN PLOT
gp_comparisons = list(c("HC", "CLBP"),
					  c("CLBP", "FM"),
					  c("HC", "FM"))

ggboxplot(dat1,
		  x = "group.factor",
		  y = "mcgill_total",
		  color =  "group.factor",
		  palette = "jco") +
	stat_compare_means(comparisons = gp_comparisons,
					   label.y = c(45, 55, 65)) +
	stat_compare_means(label.y = 80)


##			END			##
```




#PLOTS

## CORR PLOTS

```{r HC-Group, eval=FALSE, echo=FALSE, message=FALSE}
######		HC GROUP			####
dat.HC2 <- dat.HC %>% select(!"group.factor", -isi_total)
dat.HC2 <- dat.HC2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.HC2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "HC group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r CLBP-Group, eval=FALSE, echo=FALSE, message=FALSE}
######		CLBP GROUP			####
dat.CLBP2 <- dat.CLBP %>% select(!"group.factor", -isi_total)
dat.CLBP2 <- dat.CLBP2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.CLBP2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "CLBP group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r FM-Group, eval=FALSE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.FM2 <- dat.FM %>% select(!"group.factor", -isi_total)
dat.FM2 <- dat.FM2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.FM2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "FM group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r Pain-Groups, eval=FALSE, echo=FALSE, message=FALSE}
######		PAIN GROUPS			####
dat.pain2 <- dat.pain %>% select(!"group.factor", -isi_total)
dat.pain2 <- dat.pain2 %>% select(!"slpDist", -TIB)

####		PLOT R AND P VALUES IN A SINGLE GRAPH		####
###		FROM A FORUM POST IN 2019		###

####		Breaking down the plot		####

corr.data(dat.pain2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + # provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
	# This overlays a grid of varying blue and adds the "corr" legend on the right, 
	                    # and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 2, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size = 2, colour="black")  + # color of text
	# scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
	scale_fill_gradient2(low="red", mid="white", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "Both pain groups",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=3)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +



```


```{r CLBP-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.CLBP2 <- dat.CLBP %>% select(!"group.factor", -TIB)
dat.CLBP2 <- dat.CLBP2 %>% select(!"slpDist")

####		Breaking down the plot		####

corr.data(dat.CLBP2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 1.5, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=1.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "CLBP pain group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme_classic() +
	# theme_cleveland() +

```


```{r HC-corrplot, eval=FALSE, echo=FALSE, message=FALSE}
######		FM GROUP			####
dat.HC2 <- dat.HC %>% select(!"group.factor", -TIB)
dat.HC2 <- dat.HC2 %>% select(!"slpDist")

####		Breaking down the plot		####

corr.data(dat.HC2) %>% 
	ggplot(aes(colvars, fct_rev(rowvars), check_overlap = TRUE)) + 
		# provides chart area and variable names
	geom_tile(colour = "grey20", aes(fill = corr), size = 0.5) + 
			# This overlays a grid of varying blue and adds
			# the "corr" legend on the right, and adds a dark grey grid.
	# geom_point(aes(size=p.value,
	# 			   colour=cut(abs(corr), c(0, 0.01, 0.05, 1),
	# 			   		   include.lowest=TRUE)), pch=15) +
	geom_text(aes(label = sprintf("%1.2f", corr)), # add correlation values
			  position = position_nudge(y = 0.2), # position in the square for values
			  size = 1.5, # size of text
			  colour = "black") + # color of text
	geom_text(aes(label=paste0("(",sprintf("%1.2f", p.value),")")), # adds p-value to square
			  position=position_nudge(y=-0.2), # positions p-value
			  size=1.5, colour="black")  + # color of text
	scale_fill_gradient2(low="red", mid="yellow2", high="blue", # color scale for color bar
						 midpoint=0, limits=c(-1,1)) + # range of values for color bar
	scale_size_continuous(range=c(8,12)) + # I am not sure what this line does
	labs(title = "Healthy control group",
		 x="",
		 y="") +
	scale_x_discrete(guide=guide_axis(n.dodge=2)) +
	coord_fixed()
	# theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
	# theme_classic() +
	# theme_cleveland() +

```

The end of corr plots
